---
title: "APIM - Control"
author: "Pascal Küng, MSc, Patrick Höhener, MSc, James M. Allen, PhD, Robert Tobias, PhD, Urte Scholz, PhD"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_document:
    theme: flatly
    df_print: kable
    toc: yes
    toc_float:
      collapsed: false
      smooth_scroll: true
    code_folding: show
    toc_depth: 5
    highlight: tango
---


# Setup

```{r setup, warning=FALSE, message=FALSE, results='hide'}

knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(R.utils)
library(wbCorr)
library(readxl)
library(kableExtra)
library(brms)
library(bayesplot)
library(beepr)
library(DHARMa)

source(file.path('Functions', 'ReportModels.R'))
source(file.path('Functions', 'PrettyTables.R'))
source(file.path('Functions', 'ReportMeasures.R'))
source(file.path('Functions', 'PrepareData.R'))


```


```{r set_options}

system("shutdown /a")

# Set options for analysis
use_mi = FALSE
shutdown = FALSE
report_ordinal = FALSE

options(
  dplyr.print_max = 100, 
  brms.backend = 'cmdstan',
  brms.file_refit = ifelse(use_mi, 'never', 'on_change'),
  #brms.file_refit = 'always',
  error = function() beepr::beep(sound = 5)
)


```


```{r prepare_datasets, results='asis'}

df <- openxlsx::read.xlsx('long.xlsx')
df_original <- df

df_list <- prepare_data(df, use_mi = use_mi)
df_double <- df_list[[1]]
df_full <- df_list[[2]]

```



# Descriptives

# Sample Statistics

```{r describe_sample, results='asis'}

# Income (mean of both partner's report)
merge_income <- function(income1, income2) {
  merged_income <- numeric(length(income1))
  
  # Loop through each pair of incomes
  for (i in seq_along(income1)) {
    # Handle NA
    if (is.na(income1[i])) {
      merged_income[i] <- income2[i]
    } 
    
    else if (is.na(income2[i])) {
      merged_income[i] <- income1[i]
    }
    
    # if both are informative, take mean and round
    else if (income1[i] %in% 1:6 && income2[i] %in% 1:6) {
      merged_income[i] <- round((income1[i] + income2[i]) / 2)
    }
    
    # if one is informative and the other not, use the informative one. 
    else if (income1[i] %in% 1:6) {
      merged_income[i] <- income1[i]
    }
    else if (income2[i] %in% 1:6) {
      merged_income[i] <- income2[i]
    }
    
    # Now we only have cases, where both are either 70 or 99. We simply report "undisclosed". 
    else {
      merged_income[i] <- 99
    }
  }
  
  # Convert to factor
  merged_income <- factor(
    merged_income, levels = c(1,2,3,4,5,6,70,99), 
    labels = c(
      "up to CHF 2'000.-", 
      "CHF 2'001.- to CHF 4'000.-",
      "CHF 4'001.- to CHF 6'000.-",
      "CHF 6'001.- to CHF 8'000.-",
      "CHF 8'001.- to CHF 10'000.-", 
      "above CHF 10'000.-", 
      "I don't know",
      "Undisclosed"
  )
  )
  
  return(merged_income)
}



df_sample_report <- df_full %>%
  group_by(coupleID) %>%
  arrange(userID) %>%
  # Computing couple level variables
  mutate(
    Household_Income = merge_income(first(pre_income_1), last(pre_income_1)),
    
    reldur = pre_rel_duration_m / 12 + pre_rel_duration_y,
    Relationship_duration = mean(reldur, na.rm = TRUE),
    
    habdur = pre_hab_duration_m / 12 + pre_hab_duration_y,
    Cohabiting_duration = mean(habdur, na.rm = TRUE),
    
    Marital_status = factor(
      case_when(
        all(pre_mat_stat == 1) ~ "Married",
        any(pre_mat_stat == 1) ~ "One Partner Married",
        TRUE ~ "Not Married"
      )
    ),
    
    Have_children = factor(
      (first(pre_child_option) + last(pre_child_option)) > 0, 
      levels = c(FALSE, TRUE), 
      labels = c('Have Children', 'No Children')),
    
    Gender = factor(
      gender, 
      levels = c(1,2,3), 
      labels = c('Male','Female', 'Other')),
    


    Couple_type = as.factor(
      case_when(
        first(Gender) == last(Gender) & first(Gender) == 'Male' ~ 'Same-Sex Couple (Male)',
        first(Gender) == last(Gender) & first(Gender) == 'Female' ~ 'Same-Sex Couple (Female)',
        TRUE ~ 'Mixed-sex Couple'
      )
    )
  ) %>%
  ungroup() %>%
  # Individual level variables
  mutate(
    Age = pre_age,
    Handedness = factor(
      pre_handedness, 
      levels = c(0, 1, 2), 
      c('Right','Left', 'Ambidextrous')),
  Highest_Education = factor(
    pre_education, 
    levels = c(1,2,3,4,5,6,7), 
    labels = c(
      "(still) no school diploma",
      "compulsory education (9 years)",
      "vocational training (apprenticeship)",
      "Matura (university entrance qualification)",
      "Bachelor's degree", 
      "Master's degree",
      "Doctorate degree"
      )
    ),
  BMI = pre_weight / ((pre_height / 100)^2) # to meters
  ) %>%
  select(c(Relationship_duration, Cohabiting_duration, Couple_type, Household_Income, 
            Marital_status, Have_children, 
            Gender, Age, Handedness, Highest_Education, BMI))


sample_table <- report_measures(df_sample_report, ICC = F)
sample_table$n_Obs <- as.numeric(sample_table$n_Obs) / 55
rownames(sample_table) <- NULL

n_couple_vars <- 17
sample_table$n_Obs[1:n_couple_vars] <- sample_table$n_Obs[1:n_couple_vars] / 2

packing_sample <- list(
    "Couple level variables (38 couples)" = 
      c(1, n_couple_vars),
    "Individual level variables (76 individuals)" 
    = c(n_couple_vars+1, nrow(sample_table))
    ) 

df_sample_summary <- print_df(
  sample_table,
  rows_to_pack = packing_sample
)

export_xlsx(df_sample_summary,
            file.path('Output', 'SampleDescription.xlsx'),
            merge_option = 'both',
            rows_to_pack = packing_sample,
            colwidths = c(20,35,7,7,7,7,7,10)
            )

df_sample_summary

```



## Measures

### Focal Variables

```{r describe_measures_main, results='asis'}
main_constructs <- c("persuasion", "pressure","pushing", 
                     "pa_sub", "pa_obj", "aff", "reactance"
                     )

main_descriptives <- report_measures(
  data = df_full, 
  measures = main_constructs,
  ICC = TRUE, 
  cluster_var = df_full$userID)

openxlsx::write.xlsx(
  main_descriptives, 
  file.path('Output', 'DescriptivesMain.xlsx')
  )

print_df(main_descriptives)

```

### All Variables

```{r describe_measures_all, results='asis'}




all_constructs <- c(
  main_constructs,
  "day",
  "weartime",
  "isWeekend",
  "plan",
  "studyGroup",
  "support",
  "got_JITAI",
  "skilled_support"
)


all_descriptives <- report_measures(df_full, all_constructs, ICC = F)

openxlsx::write.xlsx(
  all_descriptives, 
  file.path('Output', 'DescriptivesAll.xlsx')
)

print_df(all_descriptives)

```

## Correlations

```{r correlations, results='asis'}
cors <- wbCorr(df_full[,c(main_constructs)], df_full$coupleID, method = 'spearman')

main_cors <- summary(cors, 'wb')$merged_wb


openxlsx::write.xlsx(
  main_cors, 
  file.path('Output', 'Correlations.xlsx')
)

print_df(main_cors, width = '7em')

```

Within-person correlations are above the diagonal and between-person 
correlations are below the diagonal.  
On the diagonal are intraclass correlations (ICCs)


# Modelling

```{r set_report_order_persuasion}

# For indistinguishable Dyads
model_rows_fixed <- c(
    'Intercept', 
    # '-- WITHIN PERSON MAIN EFFECTS --', 
    'persuasion_self_cw', 
    'persuasion_partner_cw', 
    'pressure_self_cw', 
    'pressure_partner_cw', 
    'pushing_self_cw', 
    'pushing_partner_cw', 
    'day', 
    'weartime_self_cw',
    
    # '-- BETWEEN PERSON MAIN EFFECTS',
    'persuasion_self_cb',
    'persuasion_partner_cb',
    'pressure_self_cb',
    'pressure_partner_cb',
    'pushing_self_cb',
    'pushing_partner_cb',
    'weartime_self_cb'
  )


model_rows_fixed_ordinal <- c(
  model_rows_fixed[1],
  'Intercept[1]',
  'Intercept[2]',
  'Intercept[3]',
  'Intercept[4]',
  'Intercept[5]',
  model_rows_fixed[2:length(model_rows_fixed)]
)

model_rows_random <- c(
  # '--------------',
  # '-- RANDOM EFFECTS --',
  'sd(Intercept)', 
  'sd(persuasion_self_cw)',
  'sd(persuasion_partner_cw)',
  'sd(pressure_self_cw)',
  'sd(pressure_partner_cw)',
  'sd(pushing_self_cw)',
  'sd(pushing_partner_cw)',
  # '-- CORRELATION STRUCTURE -- ', 
  'ar[1]', 
  'nu',
  'shape',
  'sderr',
  'sigma'
)

model_rows_random_ordinal <- c(model_rows_random,'disc')

```


```{r set_display_names}

# For indistinguishable Dyads
model_rownames_fixed <- c(
    'Intercept', 
    # '-- WITHIN PERSON MAIN EFFECTS --', 
    'Daily received persuasion target -> target', 
    'Daily received persuasion target -> agent', 
    'Daily received pressure target -> target', 
    'Daily received pressure target -> agent', 
    'Daily received pushing target -> target', 
    'Daily received pushing target -> agent', 
    'Day', 
    'Daily weartime',
    
    # '-- BETWEEN PERSON MAIN EFFECTS',
    'Mean received persuasion target -> target',
    'Mean received persuasion target -> agent',
    'Mean received pressure target -> target',
    'Mean received pressure target -> agent',
    'Mean received pushing target -> target',
    'Mean received pushing target -> agent',
    'Mean weartime'
  )


model_rownames_fixed_ordinal <- c(
  model_rownames_fixed[1],
  'Intercept[1]',
  'Intercept[2]',
  'Intercept[3]',
  'Intercept[4]',
  'Intercept[5]',
  model_rownames_fixed[2:length(model_rownames_fixed)]
)

model_rownames_random <- c(
  # '--------------',
  # '-- RANDOM EFFECTS --',
  'sd(Intercept)', 
  'sd(Daily received persuasion target -> target)', 
  'sd(Daily received persuasion target -> agent)', 
  'sd(Daily received pressure target -> target)', 
  'sd(Daily received pressure target -> agent)', 
  'sd(Daily received pushing target -> target)', 
  'sd(Daily received pushing target -> agent)', 
  # '-- CORRELATION STRUCTURE -- ', 
  'ar[1]', 
  'nu',
  'shape',
  'sderr',
  'sigma'
)

model_rownames_random_ordinal <- c(model_rownames_random,'disc')


```


```{r set_display_names_alt}

# For indistinguishable Dyads
model_rownames_fixed <- c(
    "Intercept", 
    # "-- WITHIN PERSON MAIN EFFECTS --", 
    "Daily persuasion experienced", 
    "Daily persuasion utilized (partner's view)", # OR partner received
    "Daily pressure experienced", 
    "Daily pressure utilized (partner's view)", 
    "Daily pushing experienced", 
    "Daily pushing utilized (partner's view)", 
    "Day", 
    "Daily weartime",
    
    # "-- BETWEEN PERSON MAIN EFFECTS",
    "Mean persuasion experienced", 
    "Mean persuasion utilized (partner's view)", 
    "Mean pressure experienced", 
    "Mean pressure utilized (partner's view)", 
    "Mean pushing experienced", 
    "Mean pushing utilized (partner's view)", 
    "Mean weartime"
  )


model_rownames_fixed_ordinal <- c(
  model_rownames_fixed[1],
  'Intercept[1]',
  'Intercept[2]',
  'Intercept[3]',
  'Intercept[4]',
  'Intercept[5]',
  model_rownames_fixed[2:length(model_rownames_fixed)]
)

model_rownames_random <- c(
  # '--------------',
  # '-- RANDOM EFFECTS --',
  'sd(Intercept)', 
  "sd(Daily persuasion experienced)", 
  "sd(Daily persuasion utilized (partner's view))", # OR partner received
  "sd(Daily pressure experienced)", 
  "sd(Daily pressure utilized (partner's view))", 
  "sd(Daily pushing experienced)", 
  "sd(Daily pushing utilized (partner's view))", 
  # '-- CORRELATION STRUCTURE -- ', 
  'ar[1]', 
  'nu',
  'shape',
  'sderr',
  'sigma'
)

model_rownames_random_ordinal <- c(model_rownames_random,'disc')


```


```{r parameters_for_printing}

rows_to_pack <- list(
  "Within-Person Effects" = c(2,9),
  "Between-Person Effects" = c(10,16),
  "Random Effects" = c(17, 23), 
  "Additional Parameters" = c(24,28)
  )


rows_to_pack_ordinal <- list(
  "Intercepts" = c(1,6),
  "Within-Person Effects" = c(2+5,9+5),
  "Between-Person Effects" = c(10+5,16+5),
  "Random Effects" = c(17+5, 23+5), 
  "Additional Parameters" = c(24+5,28+6)
  )

```


## Subjective MVPA

```{r explore_pa_sub_dist}

range(df_double$pa_sub, na.rm = T) 
hist(df_double$pa_sub, breaks = 100) 

```

Modelling using the gaussian family fails. 
Due to the many zeros, transformations won't help estimating the models. We employ the negative binomial family. 

```{r pa_sub, results='hide', message=FALSE, warning=FALSE}


formula <- bf(
  pa_sub ~ 
    persuasion_self_cw + persuasion_partner_cw +
    pressure_self_cw + pressure_partner_cw +
    pushing_self_cw + pushing_partner_cw +
    
    persuasion_self_cb + persuasion_partner_cb +
    pressure_self_cb + pressure_partner_cb +
    pushing_self_cb + pushing_partner_cb +
    
    day + 
    
    # Random effects
    (1 | coupleID),

  autocor = ~ ar(time = day, gr = coupleID:userID, p = 1),
  hu = ~ 1
)




prior1 <- c(
  brms::set_prior("normal(0, 2.5)", class = "b"),
  brms::set_prior("normal(0, 50)", class = "Intercept", lb = 0),
  
  brms::set_prior("normal(0, 10)", class = "sd", group = "coupleID", lb = 0),
  
  brms::set_prior("cauchy(0, 5)", class = "ar", lb = -1, ub = 1),
  brms::set_prior("cauchy(0, 20)", class = "shape"), 
  brms::set_prior("cauchy(0, 10)", class='sderr')
)


#df_minimal <- df_double[, c("AorB", all.vars(as.formula(formula)))]

pa_sub <- my_brm(
  mi = use_mi, 
  imputed_data = implist,
  
  formula = formula, 
  #prior = prior1,
  data = df_double, 
  family = brms::hurdle_lognormal(),
  #control = list(adapt_delta = 0.99),
  iter = 500,
  #warmup = 2000,
  chains = 4,
  cores = 4,
  seed = 7777,
  file = file.path("models_cache_brms", "pa_sub_hu")
)


```


```{r check_pa_sub, warning=FALSE}

plot(pa_sub, ask = FALSE)
plot(pp_check(pa_sub, type = 'ecdf_overlay'))
plot(pp_check(pa_sub))

pp_check_transformed(pa_sub, transform = log1p)

loo(pa_sub)

```



```{r report_pa_sub, results='asis', warning=FALSE}

summarize_brms(
  pa_sub, 
  model_rows_fixed = model_rows_fixed,
  model_rows_random = model_rows_random,
  model_rownames_fixed = model_rownames_fixed,
  model_rownames_random = model_rownames_random,
  exponentiate = T) %>%
  print_df(rows_to_pack = rows_to_pack)

```



## Device Based MVPA 

```{r explore_pa_obj_dist}

range(df_double$pa_obj, na.rm = T) 
hist(df_double$pa_obj, breaks = 50)

df_double$pa_obj_log <- log(df_double$pa_obj)

hist(df_double$pa_obj_log, breaks = 50)

```

We tried negative binomial here as well for consistency, but the model did not 
converge. Poisson also did not work. As we have no zeros in this distribution, 
we log transform. 



```{r pa_obj_log, results='hide', message=FALSE, warning=FALSE}

formula <- bf(
  pa_obj_log ~ 
    persuasion_self_cw + persuasion_partner_cw +
    pressure_self_cw + pressure_partner_cw +
    pushing_self_cw + pushing_partner_cw +
    
    persuasion_self_cb + persuasion_partner_cb +
    pressure_self_cb + pressure_partner_cb +
    pushing_self_cb + pushing_partner_cb +
    
    day + weartime_self_cw + weartime_self_cb +
    
    # Random effects
    (persuasion_self_cw + persuasion_partner_cw +
    pressure_self_cw + pressure_partner_cw +
    pushing_self_cw + pushing_partner_cw | coupleID),

  autocor = ~ ar(time = day, gr = coupleID:userID, p = 1)
)



prior1 <- c(
  brms::set_prior("normal(0, 2.5)", class = "b"),
  brms::set_prior("normal(0, 50)", class = "Intercept", lb = 0),
  
  brms::set_prior("normal(0, 10)", class = "sd", group = "coupleID", lb = 0),
  
  brms::set_prior("cauchy(0, 5)", class = "ar", lb = -1, ub = 1),
  brms::set_prior("cauchy(0, 10)", class = "sigma", lb = 0)
)


#df_minimal <- df_double[, c("AorB", all.vars(as.formula(formula)))]

pa_obj_log <- my_brm(
  mi = use_mi, 
  imputed_data = implist,
  
  formula = formula, 
  prior = prior1,
  data = df_double, 
  family = gaussian(),
  #control = list(adapt_delta = 0.99),
  iter = 5000,
  warmup = 2000,
  chains = 4,
  cores = 4,
  seed = 7777,
  file = file.path("models_cache_brms", "pa_obj_log")
)


```


```{r check_pa_obj_log, warning=FALSE}

plot(pa_obj_log, ask = FALSE)
plot(pp_check(pa_obj_log, type = 'ecdf_overlay'))
plot(pp_check(pa_obj_log))

#pp_check_transformed(pa_obj_log, transform = log1p)

loo(pa_obj_log)

```



```{r report_pa_obj_log, results='asis', warning=FALSE}

summarize_brms(
  pa_obj_log, 
  model_rows_fixed = model_rows_fixed,
  model_rows_random = model_rows_random,
  model_rownames_fixed = model_rownames_fixed,
  model_rownames_random = model_rownames_random,
  exponentiate = T) %>%
  print_df(rows_to_pack = rows_to_pack)

```




## Affect

```{r explore_aff_dist}

range(df_double$aff, na.rm = T) 
hist(df_double$aff, breaks = 15)

```



```{r mood, results='hide', results='hide', message=FALSE, warning=FALSE}


formula <- bf(
  aff ~ 
    persuasion_self_cw + persuasion_partner_cw +
    pressure_self_cw + pressure_partner_cw +
    pushing_self_cw + pushing_partner_cw +
    
    persuasion_self_cb + persuasion_partner_cb +
    pressure_self_cb + pressure_partner_cb +
    pushing_self_cb + pushing_partner_cb +
    
    day +
    
    # Random effects
    (persuasion_self_cw + persuasion_partner_cw +
    pressure_self_cw + pressure_partner_cw +
    pushing_self_cw + pushing_partner_cw | coupleID),

  autocor = ~ ar(time = day, gr = coupleID:userID, p = 1)
)



prior1 <- c(
  brms::set_prior("normal(0, 5)", class = "b"),
  brms::set_prior("normal(0, 20)", class = "Intercept", lb=0, ub=6), # range of the outcome scale
  
  brms::set_prior("normal(0, 2)", class = "sd", group = "coupleID", lb = 0),

  brms::set_prior("cauchy(0, 5)", class = "ar", lb = -1, ub = 1),
  brms::set_prior("cauchy(0, 10)", class = "sigma", lb = 0)
  
)

#df_minimal <- df_double[, c("AorB", all.vars(as.formula(formula)))]

mood <- my_brm(
  mi = use_mi, 
  imputed_data = implist,
  
  formula = formula, 
  prior = prior1,
  data = df_double, 
  family = gaussian(),
  #control = list(adapt_delta = 0.95, max_treedepth = 15),
  iter = 5000,
  warmup = 2000,
  chains = 4,
  cores = 4,
  seed = 7777,
  file = file.path("models_cache_brms", "mood")
)


```


```{r check_mood, warning=FALSE}

plot(mood, ask = FALSE)
plot(pp_check(mood, type = 'ecdf_overlay'))
plot(pp_check(mood))

#pp_check_transformed(mood, transform = log1p)

loo(pa_sub)

```

```{r report_mood, results='asis', warning=FALSE}

summarize_brms(
  mood, 
  model_rows_fixed = model_rows_fixed,
  model_rows_random = model_rows_random,
  model_rownames_fixed = model_rownames_fixed,
  model_rownames_random = model_rownames_random,
  exponentiate = F) %>%
  print_df(rows_to_pack = rows_to_pack)

```


## Reactance

### Gaussian

```{r explore_reactance_dist}

range(df_double$reactance, na.rm = T) 
hist(df_double$reactance, breaks = 6)

```



```{r reactance, results='hide', message=FALSE, warning=FALSE}


formula <- bf(
  reactance ~ 
    persuasion_self_cw + persuasion_partner_cw +
    pressure_self_cw + pressure_partner_cw +
    pushing_self_cw + pushing_partner_cw +
    
    persuasion_self_cb + persuasion_partner_cb +
    pressure_self_cb + pressure_partner_cb +
    pushing_self_cb + pushing_partner_cb +
    
    day +
    
    # Random effects
    (persuasion_self_cw + persuasion_partner_cw +
    pressure_self_cw + pressure_partner_cw +
    pushing_self_cw + pushing_partner_cw | coupleID),

  autocor = ~ ar(time = day, gr = coupleID:userID, p = 1)
)



prior1 <- c(
  brms::set_prior("normal(0, 5)", class = "b"),
  brms::set_prior("normal(0, 20)", class = "Intercept", lb=0, ub=5), # range of the outcome scale
  
  brms::set_prior("normal(0, 2)", class = "sd", group = "coupleID", lb = 0),

  brms::set_prior("cauchy(0, 5)", class = "ar", lb = -1, ub = 1),
  brms::set_prior("cauchy(0, 10)", class = "sigma", lb = 0)
)




#df_minimal <- df_double[, c("AorB", all.vars(as.formula(formula)))]

reactance <- my_brm(
  mi = use_mi, 
  imputed_data = implist,
  
  formula = formula, 
  prior = prior1,
  data = df_double, 
  family = gaussian(),
  #control = list(adapt_delta = 0.95, max_treedepth = 15),
  iter = 5000,
  warmup = 2000,
  chains = 4,
  cores = 4,
  seed = 7777,
  file = file.path("models_cache_brms", "reactance")
)


```


```{r check_reactance, warning=FALSE}

plot(reactance, ask = FALSE)
plot(pp_check(reactance, type = 'ecdf_overlay'))
plot(pp_check(reactance))

#pp_check_transformed(reactance, transform = log1p)

loo(reactance)

```

```{r report_reactance, results='asis', warning=FALSE}

summarize_brms(
  reactance, 
  model_rows_fixed = model_rows_fixed,
  model_rows_random = model_rows_random,
  model_rownames_fixed = model_rownames_fixed,
  model_rownames_random = model_rownames_random,
  exponentiate = F) %>%
  print_df(rows_to_pack = rows_to_pack)

```



```{r testingdifferencecoefs}

hypothesis(reactance, "pressure_self_cw > pushing_self_cw")

```



### Ordinal


```{r reactance_ordinal, results='hide', message=FALSE, warning=FALSE}

df_double$reactance_ordinal <- factor(df_double$reactance,
                                      levels = 0:5, 
                                      ordered = TRUE)

formula <- bf(
  reactance_ordinal ~ 
    persuasion_self_cw + persuasion_partner_cw +
    pressure_self_cw + pressure_partner_cw +
    pushing_self_cw + pushing_partner_cw +
    
    persuasion_self_cb + persuasion_partner_cb +
    pressure_self_cb + pressure_partner_cb +
    pushing_self_cb + pushing_partner_cb +
    
    day +
    
    # Random effects
    (persuasion_self_cw + persuasion_partner_cw +
    pressure_self_cw + pressure_partner_cw +
    pushing_self_cw + pushing_partner_cw | coupleID),

  autocor = ~ ar(time = day, gr = coupleID:userID, p = 1)
)



prior1 <- c(
  set_prior("normal(0, 2.5)", class = "b"),
  set_prior("normal(0, 5)", class = "Intercept"),
  set_prior("normal(0, 1)", class = "sd", group = "coupleID", lb = 0),
  set_prior("normal(0, 0.075)", class = "ar", lb = -1, ub = 1),
  set_prior("normal(0.5, 2.0)", class = "sderr", lb = 0)
)




#df_minimal <- df_double[, c("AorB", all.vars(as.formula(formula)))]

reactance_ordinal <- my_brm(
  mi = use_mi, 
  imputed_data = implist,
  
  formula = formula, 
  prior = prior1,
  data = df_double, 
  family = brms::cumulative(),
  control = list(adapt_delta = 0.95),
  iter = 5000,
  warmup = 2000,
  chains = 4,
  cores = 4,
  seed = 7777,
  file = file.path("models_cache_brms", "reactance_ordinal")
)


```


```{r check_reactance_ordinal, warning=FALSE}

plot(reactance_ordinal, ask = FALSE)
plot(pp_check(reactance_ordinal, type = 'ecdf_overlay'))
plot(pp_check(reactance_ordinal))

#pp_check_transformed(reactance_ordinal, transform = log1p)

loo(reactance_ordinal)
```

```{r report_reactance_ordinal, results='asis', warning=FALSE}

summarize_brms(
  reactance_ordinal, 
  model_rows_fixed = model_rows_fixed_ordinal,
  model_rows_random = model_rows_random_ordinal,
  model_rownames_fixed = model_rownames_fixed_ordinal,
  model_rownames_random = model_rownames_random_ordinal,
  exponentiate = T) %>%
  print_df(rows_to_pack = rows_to_pack_ordinal)

```

```{r testingdifferencecoefsordinal}

hypothesis(reactance_ordinal, "pressure_self_cw > pushing_self_cw")

```


### Binary 

```{r is_reactance, results='hide', message=FALSE, warning=FALSE}

introduce_binary_reactance <- function(data) {
  data$is_reactance <- factor(data$reactance > 0, levels = c(FALSE, TRUE), labels = c(0, 1))
  return(data)
}



df_double <- introduce_binary_reactance(df_double)
if (use_mi) {
  for (i in seq_along(implist)) {
    implist[[i]] <- introduce_binary_reactance(implist[[i]])
  }
}


formula <- bf(
  is_reactance ~ 
    persuasion_self_cw + persuasion_partner_cw +
    pressure_self_cw + pressure_partner_cw +
    pushing_self_cw + pushing_partner_cw +
    
    persuasion_self_cb + persuasion_partner_cb +
    pressure_self_cb + pressure_partner_cb +
    pushing_self_cb + pushing_partner_cb +
    
    day +
    
    # Random effects
    (persuasion_self_cw + persuasion_partner_cw +
    pressure_self_cw + pressure_partner_cw +
    pushing_self_cw + pushing_partner_cw | coupleID),

  autocor = ~ ar(time = day, gr = coupleID:userID, p = 1)
)



prior1 <- c(
  brms::set_prior("normal(0, 2.5)", class = "b"),
  brms::set_prior("normal(0, 10)", class = "Intercept", lb=0, ub=5), # range of the outcome scale
  
  brms::set_prior("normal(0, 2)", class = "sd", group = "coupleID", lb = 0),

  brms::set_prior("cauchy(0, 5)", class = "ar", lb = -1, ub = 1)
  #brms::set_prior("cauchy(0, 10)", class = "sigma", lb = 0)
)


#df_minimal <- df_double[, c("AorB", all.vars(as.formula(formula)))]

is_reactance <- my_brm(
  mi = use_mi, 
  imputed_data = implist,
  
  formula = formula, 
  prior = prior1,
  data = df_double, 
  family = bernoulli(),
  #control = list(adapt_delta = 0.95, max_treedepth = 15),
  iter = 5000,
  warmup = 2000,
  chains = 4,
  cores = 4,
  seed = 7777,
  file = file.path("models_cache_brms", "is_reactance")
)


```

```{r check_is_reactance, warning=FALSE}

plot(is_reactance, ask = FALSE)
plot(pp_check(is_reactance, type = 'ecdf_overlay'))
plot(pp_check(is_reactance))

#pp_check_transformed(is_reactance, transform = log1p)

loo(is_reactance)

```

```{r report_is_reactance, results='asis', warning=FALSE}

summarize_brms(
  is_reactance, 
  model_rows_fixed = model_rows_fixed,
  model_rows_random = model_rows_random,
  model_rownames_fixed = model_rownames_fixed,
  model_rownames_random = model_rownames_random,
  exponentiate = T) %>%
  print_df(rows_to_pack = rows_to_pack)

```


```{r testingdifferencecoefsbinary}

hypothesis(is_reactance, "pressure_self_cw > pushing_self_cw")

```


# Report All Models

```{r report_sidebyside, warning=FALSE}


if (report_ordinal) {
  model_rows_random_final <- model_rows_random_ordinal
  model_rows_fixed_final <- model_rows_fixed_ordinal
  model_rownames_fixed_final <- model_rownames_fixed_ordinal
  model_rownames_random_final <- model_rownames_random_ordinal
  rows_to_pack_final <- rows_to_pack_ordinal
} else {
  model_rows_random_final <- model_rows_random
  model_rows_fixed_final <- model_rows_fixed
  model_rownames_fixed_final <- model_rownames_fixed
  model_rownames_random_final <- model_rownames_random
  rows_to_pack_final <- rows_to_pack
}



all_models <- report_side_by_side(
  pa_sub,
  pa_obj_log,
  mood,
  reactance,
  is_reactance,
  
  model_rows_random = model_rows_random_final,
  model_rows_fixed = model_rows_fixed_final,
  model_rownames_random = model_rownames_random_final,
  model_rownames_fixed = model_rownames_fixed_final
) 


# pretty printing
summary_all_models <- all_models %>%
  print_df(rows_to_pack = rows_to_pack_final) %>%
  add_header_above(
    c(" ", "Subjective MVPA" = 2, 
      "Device-Based MVPA" = 2, 
      "Mood" = 2,
      "Reactance Gaussian" = 2, 
      "Reactance Dichotome" = 2)
  )

export_xlsx(
  summary_all_models, 
  rows_to_pack = rows_to_pack_final,
  file.path("Output", "AllModels.xlsx"), 
  merge_option = 'both', 
  simplify_2nd_row = TRUE,
  colwidths = c(38, 7.2, 13.3, 7.2, 13.3,7.2, 13.3,7.2, 13.3,7.2, 13.3),
  line_above_rows = c(1,2),
  line_below_rows = c(-1)
)

summary_all_models

```



```{r report_system, results='asis'}

report::report_system()
report::cite_packages()

```


```{r shut_system_down, results='hide', echo=FALSE, message=FALSE, warning=FALSE}

if (shutdown) {
  system("shutdown /s /t 180")
}

beepr::beep(sound = 3)

```


