---
title: "APIM - Control - Final Models"
author: "Pascal Küng, MSc, Patrick Höhener, MSc, James M. Allen, PhD, Robert Tobias, PhD, Urte Scholz, PhD"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_document:
    theme: flatly
    df_print: kable
    toc: yes
    toc_float:
      collapsed: false
      smooth_scroll: true
    code_folding: show
    toc_depth: 5
    highlight: tango
---

```{r setup, message=FALSE, results='hide'}

knitr::opts_chunk$set(echo = TRUE)

rm(list = ls())

#cmdstanr::set_cmdstan_path(path = "C:/Users/kueng/.cmdstan/cmdstan-2.35.0")
#cmdstanr::set_cmdstan_path(path = "C:/Users/pascku/.cmdstan/cmdstan-2.36.0")

library(tidyverse)
library(R.utils)
library(wbCorr)
library(readxl)
library(kableExtra)
library(brms)
library(bayesplot)
library(see)
library(beepr)
library(DHARMa)
library(digest)
library(psych)




source(file.path('Functions', 'ReportModels.R'))
source(file.path('Functions', 'PrettyTables.R'))
source(file.path('Functions', 'ReportMeasures.R'))
source(file.path('Functions', 'PrepareData.R'))



```


```{r set_options}

system("shutdown /a")

# Set options for analysis
use_mi = FALSE
shutdown = FALSE
report_ordinal = FALSE
do_priorsense = FALSE
get_bayesfactor = TRUE
check_models = TRUE #

if (get_bayesfactor) {
  stats_to_report <- c('CI', 'SE', 'pd', 'ROPE', 'BF', 'Rhat', 'ESS')
} else {
  stats_to_report <- c('CI', 'SE', 'pd', 'ROPE', 'Rhat', 'ESS')
}

options(
  dplyr.print_max = 100, 
  brms.backend = 'cmdstan',
  brms.file_refit = ifelse(use_mi, 'never', 'on_change'),
  brms.file_refit = 'on_change',
  #brms.file_refit = 'always',
  error = function() {
    beepr::beep(sound = 5)
    if (shutdown) {
      system("shutdown /s /t 180")
      quit(save = "no", status = 1)
    }
  }
  , es.use_symbols = TRUE
)


####################### Model parameters #######################

iterations = 12000 # 12'000 per chain to achieve 40'000
warmup = 2000 # 2000

# NO AR!!!
#corstr = 'ar'
#corstr = 'cosy_couple'
#corstr = 'cosy_couple:user'


################################################################

suffix = paste0('_AsPreregisteredAPIM_', as.character(iterations))


```


```{r prepare_datasets, results='asis'}

df <- openxlsx::read.xlsx(file.path('long.xlsx'))
df_original <- df

df_double <- prepare_data(df, recode_pushing = TRUE, use_mi = use_mi)[[1]]
summary(df_double$pushing)

```


# Prepare for APIM

```{r apim_preparations}

df_double$is_A <- ifelse(df_double$pa_obj_self_cb >= df_double$pa_obj_partner_cb, 0, 1)
df_double$is_B <- ifelse(df_double$pa_obj_self_cb < df_double$pa_obj_partner_cb, 0, 1)

```



# Modelling

## Self-Reported MVPA

### Persuasion
```{r pa_sub_lognormal_persuasion, results='hide'}


formula <- bf(
  pa_sub ~ 0 + 
    is_A + is_B + # Intercepts
    is_A:persuasion_self_cw + is_B:persuasion_self_cw + 
    is_A:persuasion_partner_cw + is_B:persuasion_partner_cw +
    
    is_A:persuasion_self_cb + is_B:persuasion_self_cb + 
    is_A:persuasion_partner_cb + is_B:persuasion_partner_cb +
    
    #is_A:plan_self + is_B:plan_self + 
    #is_A:plan_partner + is_B:plan_partner +
    is_A:day + is_B:day + 
    
    # Random effects
    (0 + 
    is_A + is_B + # Intercepts
    is_A:persuasion_self_cw + is_B:persuasion_self_cw + 
    is_A:persuasion_partner_cw + is_B:persuasion_partner_cw |dd| coupleID),
  
  hu = ~ 0 + 
    is_A + is_B + # Intercepts
    is_A:persuasion_self_cw + is_B:persuasion_self_cw + 
    is_A:persuasion_partner_cw + is_B:persuasion_partner_cw +
    
    is_A:persuasion_self_cb + is_B:persuasion_self_cb + 
    is_A:persuasion_partner_cb + is_B:persuasion_partner_cb +
    
    #is_A:plan_self + is_B:plan_self + 
    #is_A:plan_partner + is_B:plan_partner +
    is_A:day + is_B:day + 
    
    # Random effects
    (0 + 
    is_A + is_B + # Intercepts
    is_A:persuasion_self_cw + is_B:persuasion_self_cw + 
    is_A:persuasion_partner_cw + is_B:persuasion_partner_cw |dd| coupleID)
  
  , decomp = 'QR'
  #, autocor = autocor_str
) 

prior1 <- c(
  brms::set_prior("normal(0, 2.5)", class = "b")
  , brms::set_prior("normal(0, 2)", class = "b", dpar = "hu")
  
  , brms::set_prior("normal(0, 50)", class = "b", coef = 'is_A')
  , brms::set_prior("normal(0, 50)", class = "b", coef = 'is_B')
  
  , brms::set_prior("normal(0.5, 2.5)", class = "b", coef = 'is_A', dpar = 'hu')
  , brms::set_prior("normal(0.5, 2.5)", class = "b", coef = 'is_B', dpar = 'hu')
  
  , brms::set_prior("normal(0, 2)", class = "sd", group = "coupleID", lb = 0)
  , brms::set_prior("student_t(3, 0, 2.5)", class = "sigma", lb = 0)
)

#brms::validate_prior(
#  prior1, 
#  formula = formula, 
#  data = df_double, 
#  family = hurdle_lognormal()
#)

#df_minimal <- df_double[, c("AorB", all.vars(as.formula(formula)))]

pa_sub_persuasion <- my_brm(
  mi = use_mi, 
  imputed_data = implist,
  
  formula = formula, 
  prior = prior1,
  data = df_double, 
  family = brms::hurdle_lognormal(), 
  #family = brms::hurdle_negbinomial(), 
  #family = brms::hurdle_poisson(),
  #control = list(adapt_delta = 0.95, max_treedepth = 15),
  iter = iterations,
  warmup = warmup,
  chains = 4,
  cores = 4,
  seed = 42,
  file = file.path("models_cache_brms", paste0("pa_sub_hu_lognormal_persuasion", suffix))
  #, file_refit = 'always'
)


```


```{r check_pa_sub_lognormal_persuasion}
if (check_models) {
  check_brms(pa_sub_persuasion, log_pp_check = TRUE)
  DHARMa.check_brms.all(pa_sub_persuasion, integer = TRUE, outliers_type = 'bootstrap')
}
```



```{r report_pa_sub_lognormal_persuasion, results='asis', fig.width=8, fig.height=7, dpi=300}

# rope range for continuous part of the model
rope_factor <- sd(log(pa_sub_persuasion$data$pa_sub[pa_sub_persuasion$data$pa_sub > 0]))
rope_range_continuous = c(-0.1 * rope_factor, 0.1 * rope_factor)

summary_pa_sub <- summarize_brms(
  pa_sub_persuasion, 
  stats_to_report = stats_to_report,
  rope_range = rope_range_continuous,
  hu_rope_range = c(-0.18, 0.18),
  #model_rows_fixed = model_rows_fixed,
  #model_rows_random = model_rows_random,
  #model_rownames_fixed = model_rownames_fixed,
  #model_rownames_random = model_rownames_random,
  exponentiate = T) 


# Print the updated dataframe
summary_pa_sub %>%
  print_df(
    #rows_to_pack = rows_to_pack
    )


```

Hurdle part of the model on the left, non-zero part towards the right side of the table

### Pressure
```{r pa_sub_lognormal_pressure, results='hide'}


formula <- bf(
  pa_sub ~ 0 + 
    is_A + is_B + # Intercepts
    is_A:pressure_self_cw + is_B:pressure_self_cw + 
    is_A:pressure_partner_cw + is_B:pressure_partner_cw +
    
    is_A:pressure_self_cb + is_B:pressure_self_cb + 
    is_A:pressure_partner_cb + is_B:pressure_partner_cb +
    
    #is_A:plan_self + is_B:plan_self + 
    #is_A:plan_partner + is_B:plan_partner +
    is_A:day + is_B:day + 
    
    # Random effects
    (0 + 
    is_A + is_B + # Intercepts
    is_A:pressure_self_cw + is_B:pressure_self_cw + 
    is_A:pressure_partner_cw + is_B:pressure_partner_cw |dd| coupleID),
  
  hu = ~ 0 + 
    is_A + is_B + # Intercepts
    is_A:pressure_self_cw + is_B:pressure_self_cw + 
    is_A:pressure_partner_cw + is_B:pressure_partner_cw +
    
    is_A:pressure_self_cb + is_B:pressure_self_cb + 
    is_A:pressure_partner_cb + is_B:pressure_partner_cb +
    
    #is_A:plan_self + is_B:plan_self + 
    #is_A:plan_partner + is_B:plan_partner +
    is_A:day + is_B:day + 
    
    # Random effects
    (0 + 
    is_A + is_B + # Intercepts
    is_A:pressure_self_cw + is_B:pressure_self_cw + 
    is_A:pressure_partner_cw + is_B:pressure_partner_cw |dd| coupleID)
  
  , decomp = 'QR'
  #, autocor = autocor_str
) 

prior1 <- c(
  brms::set_prior("normal(0, 2.5)", class = "b")
  , brms::set_prior("normal(0, 2)", class = "b", dpar = "hu")
  
  , brms::set_prior("normal(0, 50)", class = "b", coef = 'is_A')
  , brms::set_prior("normal(0, 50)", class = "b", coef = 'is_B')
  
  , brms::set_prior("normal(0.5, 2.5)", class = "b", coef = 'is_A', dpar = 'hu')
  , brms::set_prior("normal(0.5, 2.5)", class = "b", coef = 'is_B', dpar = 'hu')
  
  , brms::set_prior("normal(0, 2)", class = "sd", group = "coupleID", lb = 0)
  , brms::set_prior("student_t(3, 0, 2.5)", class = "sigma", lb = 0)
)

#brms::validate_prior(
#  prior1, 
#  formula = formula, 
#  data = df_double, 
#  family = hurdle_lognormal()
#)

#df_minimal <- df_double[, c("AorB", all.vars(as.formula(formula)))]

pa_sub_pressure <- my_brm(
  mi = use_mi, 
  imputed_data = implist,
  
  formula = formula, 
  prior = prior1,
  data = df_double, 
  family = brms::hurdle_lognormal(), 
  #family = brms::hurdle_negbinomial(), 
  #family = brms::hurdle_poisson(),
  #control = list(adapt_delta = 0.95, max_treedepth = 15),
  iter = iterations,
  warmup = warmup,
  chains = 4,
  cores = 4,
  seed = 42,
  file = file.path("models_cache_brms", paste0("pa_sub_hu_lognormal_pressure", suffix))
  #, file_refit = 'always'
)


```


```{r check_pa_sub_lognormal_pressure}
if (check_models) {
  check_brms(pa_sub_pressure, log_pp_check = TRUE)
  DHARMa.check_brms.all(pa_sub_pressure, integer = TRUE, outliers_type = 'bootstrap')
}
```



```{r report_pa_sub_lognormal_pressure, results='asis', fig.width=8, fig.height=7, dpi=300}

# rope range for continuous part of the model
rope_factor <- sd(log(pa_sub_pressure$data$pa_sub[pa_sub_pressure$data$pa_sub > 0]))
rope_range_continuous = c(-0.1 * rope_factor, 0.1 * rope_factor)

summary_pa_sub <- summarize_brms(
  pa_sub_pressure, 
  stats_to_report = stats_to_report,
  rope_range = rope_range_continuous,
  hu_rope_range = c(-0.18, 0.18),
  #model_rows_fixed = model_rows_fixed,
  #model_rows_random = model_rows_random,
  #model_rownames_fixed = model_rownames_fixed,
  #model_rownames_random = model_rownames_random,
  exponentiate = T) 


# Print the updated dataframe
summary_pa_sub %>%
  print_df(
    #rows_to_pack = rows_to_pack
    )


```

Hurdle part of the model on the left, non-zero part towards the right side of the table

### Pushing
```{r pa_sub_lognormal_pushing, results='hide'}

formula <- bf(
  pa_sub ~ 0 + 
    is_A + is_B + # Intercepts
    is_A:pushing_self_cw + is_B:pushing_self_cw + 
    is_A:pushing_partner_cw + is_B:pushing_partner_cw +
    
    is_A:pushing_self_cb + is_B:pushing_self_cb + 
    is_A:pushing_partner_cb + is_B:pushing_partner_cb +
    
    #is_A:plan_self + is_B:plan_self + 
    #is_A:plan_partner + is_B:plan_partner +
    barriers_self_cw + barriers_self_cb + 
    is_A:day + is_B:day + 
    
    # Random effects
    (0 + 
    is_A + is_B + # Intercepts
    is_A:pushing_self_cw + is_B:pushing_self_cw + 
    is_A:pushing_partner_cw + is_B:pushing_partner_cw |dd| coupleID),
  
  hu = ~ 0 + 
    is_A + is_B + # Intercepts
    is_A:pushing_self_cw + is_B:pushing_self_cw + 
    is_A:pushing_partner_cw + is_B:pushing_partner_cw +
    
    is_A:pushing_self_cb + is_B:pushing_self_cb + 
    is_A:pushing_partner_cb + is_B:pushing_partner_cb +
    
    #is_A:plan_self + is_B:plan_self + 
    #is_A:plan_partner + is_B:plan_partner +
    is_A:day + is_B:day + 
    
    # Random effects
    (0 + 
    is_A + is_B + # Intercepts
    is_A:pushing_self_cw + is_B:pushing_self_cw + 
    is_A:pushing_partner_cw + is_B:pushing_partner_cw |dd| coupleID)
  
  , decomp = 'QR'
  #, autocor = autocor_str
) 

prior1 <- c(
  brms::set_prior("normal(0, 2.5)", class = "b")
  , brms::set_prior("normal(0, 2)", class = "b", dpar = "hu")
  
  , brms::set_prior("normal(0, 50)", class = "b", coef = 'is_A')
  , brms::set_prior("normal(0, 50)", class = "b", coef = 'is_B')
  
  , brms::set_prior("normal(0.5, 2.5)", class = "b", coef = 'is_A', dpar = 'hu')
  , brms::set_prior("normal(0.5, 2.5)", class = "b", coef = 'is_B', dpar = 'hu')
  
  , brms::set_prior("normal(0, 2)", class = "sd", group = "coupleID", lb = 0)
  , brms::set_prior("student_t(3, 0, 2.5)", class = "sigma", lb = 0)
)

#brms::validate_prior(
#  prior1, 
#  formula = formula, 
#  data = df_double, 
#  family = hurdle_lognormal()
#)

#df_minimal <- df_double[, c("AorB", all.vars(as.formula(formula)))]

pa_sub_pushing <- my_brm(
  mi = use_mi, 
  imputed_data = implist,
  
  formula = formula, 
  prior = prior1,
  data = df_double, 
  family = brms::hurdle_lognormal(), 
  #family = brms::hurdle_negbinomial(), 
  #family = brms::hurdle_poisson(),
  #control = list(adapt_delta = 0.95, max_treedepth = 15),
  iter = iterations,
  warmup = warmup,
  chains = 4,
  cores = 4,
  seed = 42,
  file = file.path("models_cache_brms", paste0("pa_sub_hu_lognormal_pushing", suffix))
  #, file_refit = 'always'
)


```


```{r check_pa_sub_lognormal_pushing}
if (check_models) {
  check_brms(pa_sub_pushing, log_pp_check = TRUE)
  DHARMa.check_brms.all(pa_sub_pushing, integer = TRUE, outliers_type = 'bootstrap')
}
```



```{r report_pa_sub_lognormal_pushing, results='asis', fig.width=8, fig.height=7, dpi=300}

# rope range for continuous part of the model
rope_factor <- sd(log(pa_sub_pushing$data$pa_sub[pa_sub_pushing$data$pa_sub > 0]))
rope_range_continuous = c(-0.1 * rope_factor, 0.1 * rope_factor)

summary_pa_sub <- summarize_brms(
  pa_sub_pushing, 
  stats_to_report = stats_to_report,
  rope_range = rope_range_continuous,
  hu_rope_range = c(-0.18, 0.18),
  #model_rows_fixed = model_rows_fixed,
  #model_rows_random = model_rows_random,
  #model_rownames_fixed = model_rownames_fixed,
  #model_rownames_random = model_rownames_random,
  exponentiate = T) 


# Print the updated dataframe
summary_pa_sub %>%
  print_df(
    #rows_to_pack = rows_to_pack
    )


```

Hurdle part of the model on the left, non-zero part towards the right side of the table



## Device Based MVPA 

```{r explore_pa_obj_dist}

range(df_double$pa_obj, na.rm = T) 

hist(df_double$pa_obj, breaks = 50)

df_double$pa_obj_log <- log(df_double$pa_obj)

hist(df_double$pa_obj_log, breaks = 50)

```



### Persuasion

```{r pa_obj_log_g_persuasion, results='hide', message=FALSE}

formula <- bf(
  pa_obj ~ 0 + 
    is_A + is_B + # Intercepts
    is_A:persuasion_self_cw + is_B:persuasion_self_cw + 
    is_A:persuasion_partner_cw + is_B:persuasion_partner_cw +
    
    is_A:persuasion_self_cb + is_B:persuasion_self_cb + 
    is_A:persuasion_partner_cb + is_B:persuasion_partner_cb +
    
    #is_A:plan_self + is_B:plan_self + 
    #is_A:plan_partner + is_B:plan_partner +
    is_A:day + is_B:day + 
    
    is_A:weartime_self_cw + is_B:weartime_self_cw + 
    is_A:weartime_self_cb + is_B:weartime_self_cb +
    
    # Random effects
    (0 + 
    is_A + is_B + # Intercepts
    is_A:persuasion_self_cw + is_B:persuasion_self_cw + 
    is_A:persuasion_partner_cw + is_B:persuasion_partner_cw |dd| coupleID)
  
  , decomp = 'QR'
  #, autocor = autocor_str
)



prior1 <- c(
  brms::set_prior("normal(0, 2.5)", class = "b")
  
  , brms::set_prior("normal(0, 50)", class = "b", coef = 'is_A')
  , brms::set_prior("normal(0, 50)", class = "b", coef = 'is_B')
  
  , brms::set_prior("normal(0, 2)", class = "sd", group = "coupleID", lb = 0)
  , brms::set_prior("student_t(3, 0, 2.5)", class = "sigma", lb = 0)
)


#brms::validate_prior(
#  prior1, 
#  formula = formula, 
#  data = df_double, 
#  family = lognormal()
#  )

#df_minimal <- df_double[, c("AorB", all.vars(as.formula(formula)))]

pa_obj_log_persuasion <- my_brm(
  mi = use_mi, 
  imputed_data = implist,
  
  formula = formula, 
  prior = prior1,
  data = df_double, 
  family = lognormal(),
  #control = list(adapt_delta = 0.95),
  iter = iterations,
  warmup = warmup,
  chains = 4,
  cores = 4,
  seed = 7777,
  file = file.path("models_cache_brms", paste0("pa_obj_log_gaussian_persuasion", suffix))
)


```


```{r check_pa_obj_log_g_persuasion}
if (check_models) {
  check_brms(pa_obj_log_persuasion, log_pp_check = TRUE)
  DHARMa.check_brms.all(pa_obj_log_persuasion, integer = TRUE, outliers_type = 'bootstrap')
}
```


```{r report_pa_obj_log_g_persuasion, results='asis'}

# rope range for lognormal model
rope_factor <- sd(log(pa_obj_log_persuasion$data$pa_obj))
rope_range_log = c(-0.1 * rope_factor, 0.1 * rope_factor)

summary_pa_obj <- summarize_brms(
  pa_obj_log_persuasion, 
  stats_to_report = stats_to_report,
  rope_range = rope_range_log,
  #model_rows_fixed = model_rows_fixed,
  #model_rows_random = model_rows_random,
  #model_rownames_fixed = model_rownames_fixed,
  #model_rownames_random = model_rownames_random,
  exponentiate = T) 

summary_pa_obj %>%
  print_df(
    #rows_to_pack = rows_to_pack
    )


```

### Pressure

```{r pa_obj_log_g_pressure, results='hide', message=FALSE}

formula <- bf(
  pa_obj ~ 0 + 
    is_A + is_B + # Intercepts
    is_A:pressure_self_cw + is_B:pressure_self_cw + 
    is_A:pressure_partner_cw + is_B:pressure_partner_cw +
    
    is_A:pressure_self_cb + is_B:pressure_self_cb + 
    is_A:pressure_partner_cb + is_B:pressure_partner_cb +
    
    #is_A:plan_self + is_B:plan_self + 
    #is_A:plan_partner + is_B:plan_partner +
    is_A:day + is_B:day + 
    
    is_A:weartime_self_cw + is_B:weartime_self_cw + 
    is_A:weartime_self_cb + is_B:weartime_self_cb +
    
    # Random effects
    (0 + 
    is_A + is_B + # Intercepts
    is_A:pressure_self_cw + is_B:pressure_self_cw + 
    is_A:pressure_partner_cw + is_B:pressure_partner_cw |dd| coupleID)
  
  , decomp = 'QR'
  #, autocor = autocor_str
)



prior1 <- c(
  brms::set_prior("normal(0, 2.5)", class = "b")
  
  , brms::set_prior("normal(0, 50)", class = "b", coef = 'is_A')
  , brms::set_prior("normal(0, 50)", class = "b", coef = 'is_B')
  
  , brms::set_prior("normal(0, 2)", class = "sd", group = "coupleID", lb = 0)
  , brms::set_prior("student_t(3, 0, 2.5)", class = "sigma", lb = 0)
)


#brms::validate_prior(
#  prior1, 
#  formula = formula, 
#  data = df_double, 
#  family = lognormal()
#  )

#df_minimal <- df_double[, c("AorB", all.vars(as.formula(formula)))]

pa_obj_log_pressure <- my_brm(
  mi = use_mi, 
  imputed_data = implist,
  
  formula = formula, 
  prior = prior1,
  data = df_double, 
  family = lognormal(),
  #control = list(adapt_delta = 0.95),
  iter = iterations,
  warmup = warmup,
  chains = 4,
  cores = 4,
  seed = 7777,
  file = file.path("models_cache_brms", paste0("pa_obj_log_gaussian_pressure", suffix))
)


```


```{r check_pa_obj_log_g_pressure}
if (check_models) {
  check_brms(pa_obj_log_pressure, log_pp_check = TRUE)
  DHARMa.check_brms.all(pa_obj_log_pressure, integer = TRUE, outliers_type = 'bootstrap')
}
```


```{r report_pa_obj_log_g_pressure, results='asis'}

# rope range for lognormal model
rope_factor <- sd(log(pa_obj_log_pressure$data$pa_obj))
rope_range_log = c(-0.1 * rope_factor, 0.1 * rope_factor)

summary_pa_obj <- summarize_brms(
  pa_obj_log_pressure, 
  stats_to_report = stats_to_report,
  rope_range = rope_range_log,
  #model_rows_fixed = model_rows_fixed,
  #model_rows_random = model_rows_random,
  #model_rownames_fixed = model_rownames_fixed,
  #model_rownames_random = model_rownames_random,
  exponentiate = T) 

summary_pa_obj %>%
  print_df(
    #rows_to_pack = rows_to_pack
    )


```

### Pushing

```{r pa_obj_log_g_pushing, results='hide', message=FALSE}

formula <- bf(
  pa_obj ~ 0 + 
    is_A + is_B + # Intercepts
    is_A:pushing_self_cw + is_B:pushing_self_cw + 
    is_A:pushing_partner_cw + is_B:pushing_partner_cw +
    
    is_A:pushing_self_cb + is_B:pushing_self_cb + 
    is_A:pushing_partner_cb + is_B:pushing_partner_cb +
    
    #is_A:plan_self + is_B:plan_self + 
    #is_A:plan_partner + is_B:plan_partner +
    barriers_self_cw + barriers_self_cb + 
    is_A:day + is_B:day + 
    
    is_A:weartime_self_cw + is_B:weartime_self_cw + 
    is_A:weartime_self_cb + is_B:weartime_self_cb +
    
    # Random effects
    (0 + 
    is_A + is_B + # Intercepts
    is_A:pushing_self_cw + is_B:pushing_self_cw + 
    is_A:pushing_partner_cw + is_B:pushing_partner_cw |dd| coupleID)
  
  , decomp = 'QR'
  #, autocor = autocor_str
)



prior1 <- c(
  brms::set_prior("normal(0, 2.5)", class = "b")
  
  , brms::set_prior("normal(0, 50)", class = "b", coef = 'is_A')
  , brms::set_prior("normal(0, 50)", class = "b", coef = 'is_B')
  
  , brms::set_prior("normal(0, 2)", class = "sd", group = "coupleID", lb = 0)
  , brms::set_prior("student_t(3, 0, 2.5)", class = "sigma", lb = 0)
)


#brms::validate_prior(
#  prior1, 
#  formula = formula, 
#  data = df_double, 
#  family = lognormal()
#  )

#df_minimal <- df_double[, c("AorB", all.vars(as.formula(formula)))]

pa_obj_log_pushing <- my_brm(
  mi = use_mi, 
  imputed_data = implist,
  
  formula = formula, 
  prior = prior1,
  data = df_double, 
  family = lognormal(),
  #control = list(adapt_delta = 0.95),
  iter = iterations,
  warmup = warmup,
  chains = 4,
  cores = 4,
  seed = 7777,
  file = file.path("models_cache_brms", paste0("pa_obj_log_gaussian_pushing", suffix))
)


```


```{r check_pa_obj_log_g_pushing}
if (check_models) {
  check_brms(pa_obj_log_pushing, log_pp_check = TRUE)
  DHARMa.check_brms.all(pa_obj_log_pushing, integer = TRUE, outliers_type = 'bootstrap')
}
```


```{r report_pa_obj_log__pushing, results='asis'}

# rope range for lognormal model
rope_factor <- sd(log(pa_obj_log_pushing$data$pa_obj))
rope_range_log = c(-0.1 * rope_factor, 0.1 * rope_factor)

summary_pa_obj <- summarize_brms(
  pa_obj_log_pushing, 
  stats_to_report = stats_to_report,
  rope_range = rope_range_log,
  #model_rows_fixed = model_rows_fixed,
  #model_rows_random = model_rows_random,
  #model_rownames_fixed = model_rownames_fixed,
  #model_rownames_random = model_rownames_random,
  exponentiate = T) 

summary_pa_obj %>%
  print_df(
    #rows_to_pack = rows_to_pack
    )


```


## Affect

```{r explore_aff_dist}

range(df_double$aff, na.rm = T)
hist(df_double$aff, breaks = 15)

```



### Persuasion

```{r mood_gauss_persuasion, results='hide', results='hide', message=FALSE}


formula <- bf(
  aff ~ 0 + 
    is_A + is_B + # Intercepts
    is_A:persuasion_self_cw + is_B:persuasion_self_cw + 
    is_A:persuasion_partner_cw + is_B:persuasion_partner_cw +
    
    is_A:persuasion_self_cb + is_B:persuasion_self_cb + 
    is_A:persuasion_partner_cb + is_B:persuasion_partner_cb +
    
    #is_A:plan_self + is_B:plan_self + 
    #is_A:plan_partner + is_B:plan_partner +
    is_A:day + is_B:day + 
    
    # Random effects
    (0 + 
    is_A + is_B + # Intercepts
    is_A:pushing_self_cw + is_B:pushing_self_cw + 
    is_A:pushing_partner_cw + is_B:pushing_partner_cw |dd| coupleID)
  
  , decomp = 'QR'
  #, autocor = autocor_str
)


prior1 <- c(
  brms::set_prior("normal(0, 5)", class = "b")
  
  , brms::set_prior("normal(0, 20)", class = "b", coef = 'is_A')
  , brms::set_prior("normal(0, 20)", class = "b", coef = 'is_B')
  
  , brms::set_prior("normal(0, 2)", class = "sd", group = "coupleID", lb = 0)
  , brms::set_prior("student_t(3, 0, 2.5)", class = "sigma", lb = 0)
)

#brms::validate_prior(
#  prior1, 
#  formula = formula, 
#  data = df_double, 
#  family = gaussian()
#  )

#df_minimal <- df_double[, c("AorB", all.vars(as.formula(formula)))]

mood_gauss_persuasion <- my_brm(
  mi = use_mi, 
  imputed_data = implist,
  
  formula = formula, 
  prior = prior1,
  data = df_double, 
  family = gaussian(),
  #control = list(adapt_delta = 0.95, max_treedepth = 15),
  iter = iterations,
  warmup = warmup,
  chains = 4,
  cores = 4,
  seed = 7777,
  file = file.path("models_cache_brms", paste0("mood_gauss_persuasion", suffix))
)


```


```{r check_mood_gauss_persuasion}
if (check_models) {
  check_brms(mood_gauss_persuasion, log_pp_check = FALSE)
  DHARMa.check_brms.all(mood_gauss_persuasion, integer = FALSE)
}
```



```{r report_mood_gauss_persuasion, results='asis', fig.width=8, fig.height=6, dpi=300}

summary_mood <- summarize_brms(
  mood_gauss_persuasion, 
  stats_to_report = stats_to_report,
  #model_rows_fixed = model_rows_fixed,
  #model_rows_random = model_rows_random,
  #model_rownames_fixed = model_rownames_fixed,
  #model_rownames_random = model_rownames_random,
  exponentiate = F) 

summary_mood %>%
  print_df(
    #rows_to_pack = rows_to_pack
    )


```



### Pressure

```{r mood_gauss_pressure, results='hide', results='hide', message=FALSE}


formula <- bf(
  aff ~ 0 + 
    is_A + is_B + # Intercepts
    is_A:pressure_self_cw + is_B:pressure_self_cw + 
    is_A:pressure_partner_cw + is_B:pressure_partner_cw +
    
    is_A:pressure_self_cb + is_B:pressure_self_cb + 
    is_A:pressure_partner_cb + is_B:pressure_partner_cb +
    
    #is_A:plan_self + is_B:plan_self + 
    #is_A:plan_partner + is_B:plan_partner +
    is_A:day + is_B:day + 
    
    # Random effects
    (0 + 
    is_A + is_B + # Intercepts
    is_A:pushing_self_cw + is_B:pushing_self_cw + 
    is_A:pushing_partner_cw + is_B:pushing_partner_cw |dd| coupleID)
  
  , decomp = 'QR'
  #, autocor = autocor_str
)


prior1 <- c(
  brms::set_prior("normal(0, 5)", class = "b")
  
  , brms::set_prior("normal(0, 20)", class = "b", coef = 'is_A')
  , brms::set_prior("normal(0, 20)", class = "b", coef = 'is_B')
  
  , brms::set_prior("normal(0, 2)", class = "sd", group = "coupleID", lb = 0)
  , brms::set_prior("student_t(3, 0, 2.5)", class = "sigma", lb = 0)
)

#brms::validate_prior(
#  prior1, 
#  formula = formula, 
#  data = df_double, 
#  family = gaussian()
#  )

#df_minimal <- df_double[, c("AorB", all.vars(as.formula(formula)))]

mood_gauss_pressure <- my_brm(
  mi = use_mi, 
  imputed_data = implist,
  
  formula = formula, 
  prior = prior1,
  data = df_double, 
  family = gaussian(),
  #control = list(adapt_delta = 0.95, max_treedepth = 15),
  iter = iterations,
  warmup = warmup,
  chains = 4,
  cores = 4,
  seed = 7777,
  file = file.path("models_cache_brms", paste0("mood_gauss_pressure", suffix))
)


```


```{r check_mood_gauss_pressure}
if (check_models) {
  check_brms(mood_gauss_pressure, log_pp_check = FALSE)
  DHARMa.check_brms.all(mood_gauss_pressure, integer = FALSE)
}
```



```{r report_mood_gauss_pressure, results='asis', fig.width=8, fig.height=6, dpi=300}

summary_mood <- summarize_brms(
  mood_gauss_pressure, 
  stats_to_report = stats_to_report,
  #model_rows_fixed = model_rows_fixed,
  #model_rows_random = model_rows_random,
  #model_rownames_fixed = model_rownames_fixed,
  #model_rownames_random = model_rownames_random,
  exponentiate = F) 

summary_mood %>%
  print_df(
    #rows_to_pack = rows_to_pack
    )


```


### pushing

```{r mood_gauss_pushing, results='hide', results='hide', message=FALSE}


formula <- bf(
  aff ~ 0 + 
    is_A + is_B + # Intercepts
    is_A:pushing_self_cw + is_B:pushing_self_cw + 
    is_A:pushing_partner_cw + is_B:pushing_partner_cw +
    
    is_A:pushing_self_cb + is_B:pushing_self_cb + 
    is_A:pushing_partner_cb + is_B:pushing_partner_cb +
    
    #is_A:plan_self + is_B:plan_self + 
    #is_A:plan_partner + is_B:plan_partner +
    barriers_self_cw + barriers_self_cb + 
    is_A:day + is_B:day + 
    
    # Random effects
    (0 + 
    is_A + is_B + # Intercepts
    is_A:pushing_self_cw + is_B:pushing_self_cw + 
    is_A:pushing_partner_cw + is_B:pushing_partner_cw |dd| coupleID)
  
  , decomp = 'QR'
  #, autocor = autocor_str
)


prior1 <- c(
  brms::set_prior("normal(0, 5)", class = "b")
  
  , brms::set_prior("normal(0, 20)", class = "b", coef = 'is_A')
  , brms::set_prior("normal(0, 20)", class = "b", coef = 'is_B')
  
  , brms::set_prior("normal(0, 2)", class = "sd", group = "coupleID", lb = 0)
  , brms::set_prior("student_t(3, 0, 2.5)", class = "sigma", lb = 0)
)

#brms::validate_prior(
#  prior1, 
#  formula = formula, 
#  data = df_double, 
#  family = gaussian()
#  )

#df_minimal <- df_double[, c("AorB", all.vars(as.formula(formula)))]

mood_gauss_pushing <- my_brm(
  mi = use_mi, 
  imputed_data = implist,
  
  formula = formula, 
  prior = prior1,
  data = df_double, 
  family = gaussian(),
  #control = list(adapt_delta = 0.95, max_treedepth = 15),
  iter = iterations,
  warmup = warmup,
  chains = 4,
  cores = 4,
  seed = 7777,
  file = file.path("models_cache_brms", paste0("mood_gauss_pushing", suffix))
)


```


```{r check_mood_gauss_pushing}
if (check_models) {
  check_brms(mood_gauss_pushing, log_pp_check = FALSE)
  DHARMa.check_brms.all(mood_gauss_pushing, integer = FALSE)
}
```



```{r report_mood_gauss_pushing, results='asis', fig.width=8, fig.height=6, dpi=300}

summary_mood <- summarize_brms(
  mood_gauss_pushing, 
  stats_to_report = stats_to_report,
  #model_rows_fixed = model_rows_fixed,
  #model_rows_random = model_rows_random,
  #model_rownames_fixed = model_rownames_fixed,
  #model_rownames_random = model_rownames_random,
  exponentiate = F) 

summary_mood %>%
  print_df(
    #rows_to_pack = rows_to_pack
    )


```



## Reactance

```{r investigatee_reactance}

range(df_double$reactance, na.rm = T) 
hist(df_double$reactance, breaks = 7) 

hist(log(df_double$reactance+0.1), breaks = 10)

```

```{r is_reactance_persuasion, results='hide', message=FALSE}
introduce_binary_reactance <- function(data) {
  data$is_reactance <- factor(data$reactance > 0, levels = c(FALSE, TRUE), labels = c(0, 1))
  return(data)
}

df_double <- introduce_binary_reactance(df_double)
if (use_mi) {
  for (i in seq_along(implist)) {
    implist[[i]] <- introduce_binary_reactance(implist[[i]])
  }
}
```



### Persuasion 

```{r is_reactance_persuasion2, results='hide', message=FALSE}
formula <- bf(
  is_reactance ~ 0 + 
    is_A + is_B + # Intercepts
    is_A:persuasion_self_cw + is_B:persuasion_self_cw + 
    is_A:persuasion_partner_cw + is_B:persuasion_partner_cw +
    
    is_A:persuasion_self_cb + is_B:persuasion_self_cb + 
    is_A:persuasion_partner_cb + is_B:persuasion_partner_cb +
    
    #is_A:plan_self + is_B:plan_self + 
    #is_A:plan_partner + is_B:plan_partner +
    is_A:day + is_B:day + 
    
    # Random effects
    (0 + 
    is_A + is_B + # Intercepts
    is_A:persuasion_self_cw + is_B:persuasion_self_cw + 
    is_A:persuasion_partner_cw + is_B:persuasion_partner_cw |dd| coupleID)
  
  , decomp = 'QR'
  #, autocor = autocor_str
  )



prior1 <- c(
  brms::set_prior("normal(0, 2.5)", class = "b")

  , brms::set_prior("normal(0, 10)", class = "b", coef = 'is_A')
  , brms::set_prior("normal(0, 10)", class = "b", coef = 'is_B')
  
  , brms::set_prior("normal(0, 2)", class = "sd", group = "coupleID", lb = 0)
)


#brms::validate_prior(
#  prior1, 
#  formula = formula, 
#  data = df_double, 
#  family = bernoulli()
#  )



#df_minimal <- df_double[, c("AorB", all.vars(as.formula(formula)))]

is_reactance_persuasion <- my_brm(
  mi = use_mi, 
  imputed_data = implist,
  
  formula = formula, 
  prior = prior1,
  data = df_double, 
  family = brms::bernoulli(),
  #control = list(adapt_delta = 0.95, max_treedepth = 15),
  iter = iterations,
  warmup = warmup,
  chains = 4,
  cores = 4,
  seed = 7777,
  file = file.path("models_cache_brms", paste0("is_reactance_persuasion", suffix))
  #, file_refit = 'always'
)


```

```{r check_is_reactance_persuasion}
if (check_models) {
  check_brms(is_reactance_persuasion)
  DHARMa.check_brms.all(is_reactance_persuasion, integer = FALSE)
}
```



```{r report_is_reactance_persuasion, results='asis', fig.width=8, fig.height=6, dpi=300}

summary_is_reactance <- summarize_brms(
  is_reactance_persuasion, 
  stats_to_report = stats_to_report,
  #model_rows_fixed = model_rows_fixed,
  #model_rows_random = model_rows_random,
  #model_rownames_fixed = model_rownames_fixed,
  #model_rownames_random = model_rownames_random,
  exponentiate = T) 

summary_is_reactance %>%
  print_df(
    #rows_to_pack = rows_to_pack
    )


```



### Pressure 

```{r is_reactance_pressure2, results='hide', message=FALSE}
formula <- bf(
  is_reactance ~ 0 + 
    is_A + is_B + # Intercepts
    is_A:pressure_self_cw + is_B:pressure_self_cw + 
    is_A:pressure_partner_cw + is_B:pressure_partner_cw +
    
    is_A:pressure_self_cb + is_B:pressure_self_cb + 
    is_A:pressure_partner_cb + is_B:pressure_partner_cb +
    
    #is_A:plan_self + is_B:plan_self + 
    #is_A:plan_partner + is_B:plan_partner +
    is_A:day + is_B:day + 
    
    # Random effects
    (0 + 
    is_A + is_B + # Intercepts
    is_A:pressure_self_cw + is_B:pressure_self_cw + 
    is_A:pressure_partner_cw + is_B:pressure_partner_cw |dd| coupleID)
  
  , decomp = 'QR'
  #, autocor = autocor_str
  )



prior1 <- c(
  brms::set_prior("normal(0, 2.5)", class = "b")

  , brms::set_prior("normal(0, 10)", class = "b", coef = 'is_A')
  , brms::set_prior("normal(0, 10)", class = "b", coef = 'is_B')
  
  , brms::set_prior("normal(0, 2)", class = "sd", group = "coupleID", lb = 0)
)


#brms::validate_prior(
#  prior1, 
#  formula = formula, 
#  data = df_double, 
#  family = bernoulli()
#  )



#df_minimal <- df_double[, c("AorB", all.vars(as.formula(formula)))]

is_reactance_pressure <- my_brm(
  mi = use_mi, 
  imputed_data = implist,
  
  formula = formula, 
  prior = prior1,
  data = df_double, 
  family = brms::bernoulli(),
  #control = list(adapt_delta = 0.95, max_treedepth = 15),
  iter = iterations,
  warmup = warmup,
  chains = 4,
  cores = 4,
  seed = 7777,
  file = file.path("models_cache_brms", paste0("is_reactance_pressure", suffix))
  #, file_refit = 'always'
)


```

```{r check_is_reactance_pressure}
if (check_models) {
  check_brms(is_reactance_pressure)
  DHARMa.check_brms.all(is_reactance_pressure, integer = FALSE)
}
```



```{r report_is_reactance_pressure, results='asis', fig.width=8, fig.height=6, dpi=300}

summary_is_reactance <- summarize_brms(
  is_reactance_pressure, 
  stats_to_report = stats_to_report,
  #model_rows_fixed = model_rows_fixed,
  #model_rows_random = model_rows_random,
  #model_rownames_fixed = model_rownames_fixed,
  #model_rownames_random = model_rownames_random,
  exponentiate = T) 

summary_is_reactance %>%
  print_df(
    #rows_to_pack = rows_to_pack
    )


```



### pushing 

```{r is_reactance_pushing2, results='hide', message=FALSE}
formula <- bf(
  is_reactance ~ 0 + 
    is_A + is_B + # Intercepts
    is_A:pushing_self_cw + is_B:pushing_self_cw + 
    is_A:pushing_partner_cw + is_B:pushing_partner_cw +
    
    is_A:pushing_self_cb + is_B:pushing_self_cb + 
    is_A:pushing_partner_cb + is_B:pushing_partner_cb +
    
    #is_A:plan_self + is_B:plan_self + 
    #is_A:plan_partner + is_B:plan_partner +
    barriers_self_cw + barriers_self_cb + 
    is_A:day + is_B:day + 
    
    # Random effects
    (0 + 
    is_A + is_B + # Intercepts
    is_A:pushing_self_cw + is_B:pushing_self_cw + 
    is_A:pushing_partner_cw + is_B:pushing_partner_cw |dd| coupleID)
  
  , decomp = 'QR'
  #, autocor = autocor_str
  )



prior1 <- c(
  brms::set_prior("normal(0, 2.5)", class = "b")

  , brms::set_prior("normal(0, 10)", class = "b", coef = 'is_A')
  , brms::set_prior("normal(0, 10)", class = "b", coef = 'is_B')
  
  , brms::set_prior("normal(0, 2)", class = "sd", group = "coupleID", lb = 0)
)


#brms::validate_prior(
#  prior1, 
#  formula = formula, 
#  data = df_double, 
#  family = bernoulli()
#  )



#df_minimal <- df_double[, c("AorB", all.vars(as.formula(formula)))]

is_reactance_pushing <- my_brm(
  mi = use_mi, 
  imputed_data = implist,
  
  formula = formula, 
  prior = prior1,
  data = df_double, 
  family = brms::bernoulli(),
  #control = list(adapt_delta = 0.95, max_treedepth = 15),
  iter = iterations,
  warmup = warmup,
  chains = 4,
  cores = 4,
  seed = 7777,
  file = file.path("models_cache_brms", paste0("is_reactance_pushing", suffix))
  #, file_refit = 'always'
)


```

```{r check_is_reactance_pushing}
if (check_models) {
  check_brms(is_reactance_pushing)
  DHARMa.check_brms.all(is_reactance_pushing, integer = FALSE)
}
```



```{r report_is_reactance_pushing, results='asis', fig.width=8, fig.height=6, dpi=300}

summary_is_reactance <- summarize_brms(
  is_reactance_pushing, 
  stats_to_report = stats_to_report,
  #model_rows_fixed = model_rows_fixed,
  #model_rows_random = model_rows_random,
  #model_rownames_fixed = model_rownames_fixed,
  #model_rownames_random = model_rownames_random,
  exponentiate = T) 

summary_is_reactance %>%
  print_df(
    #rows_to_pack = rows_to_pack
    )


```





```{r report_system, results='asis'}

report::report_system()
report::report_packages()
report::cite_packages()

```


```{r shut_system_down, results='hide', echo=FALSE, message=FALSE}

if (shutdown) {
  system("shutdown /s /t 180")
}

beepr::beep(sound = 3)

```


