---
title: "Social Control - Final Models"
author: "Pascal Küng, MSc, Patrick Höhener, MSc, James M. Allen, PhD, Robert Tobias, PhD, Urte Scholz, PhD"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_document:
    theme: flatly
    df_print: kable
    toc: yes
    toc_float:
      collapsed: false
      smooth_scroll: true
    code_folding: show
    toc_depth: 5
    highlight: tango
---

```{r setup, message=FALSE, results='hide'}

knitr::opts_chunk$set(echo = TRUE)

rm(list = ls())

#cmdstanr::set_cmdstan_path(path = "C:/Users/kueng/.cmdstan/cmdstan-2.35.0")
#cmdstanr::set_cmdstan_path(path = "C:/Users/pascku/.cmdstan/cmdstan-2.36.0")

library(tidyverse)
library(R.utils)
library(wbCorr)
library(readxl)
library(kableExtra)
library(brms)
library(bayesplot)
library(see)
library(beepr)
library(DHARMa)
library(digest)
library(tidybayes)
library(ggplot2)



source(file.path('Functions', 'ReportModels.R'))
source(file.path('Functions', 'PrettyTables.R'))
source(file.path('Functions', 'ReportMeasures.R'))
source(file.path('Functions', 'PrepareData.R'))

report_function_hash <- digest::digest(summarize_brms)



```


```{r set_options}

system("shutdown /a")

# Set options for analysis
use_mi = FALSE
shutdown = FALSE
report_ordinal = FALSE
do_priorsense = FALSE
get_bayesfactor = FALSE
check_models = FALSE 

if (get_bayesfactor) {
  stats_to_report <- c('CI', 'SE', 'pd', 'ROPE', 'BF', 'Rhat', 'ESS')
} else {
  stats_to_report <- c('CI', 'SE', 'pd', 'ROPE', 'Rhat', 'ESS')
}

options(
  dplyr.print_max = 100, 
  brms.backend = 'cmdstan',
  brms.file_refit = ifelse(use_mi, 'never', 'on_change'),
  brms.file_refit = 'on_change',
  #brms.file_refit = 'always',
  error = function() {
    beepr::beep(sound = 5)
    if (shutdown) {
      system("shutdown /s /t 180")
      quit(save = "no", status = 1)
    }
  }
  , es.use_symbols = TRUE
)


####################### Model parameters #######################

iterations = 12000 # 12'000 per chain to achieve 40'000
warmup = 2000 # 2000

# NO AR!!!
#corstr = 'ar'
#corstr = 'cosy_couple'
#corstr = 'cosy_couple:user'


################################################################

suffix = paste0('_final_with_plan_and_barriers_INTERACTION', as.character(iterations))


```


```{r prepare_datasets, results='asis'}

df <- openxlsx::read.xlsx(file.path('long.xlsx'))
df_original <- df

df_double <- prepare_data(df, recode_pushing = TRUE, use_mi = use_mi)[[1]]
summary(df_double$pushing)

```


# Modelling

```{r set_report_order_persuasion}

# For indistinguishable Dyads
model_rows_fixed <- c(
    'Intercept', 
    # '-- WITHIN PERSON MAIN EFFECTS --', 
    'persuasion_self_cw', 
    'persuasion_partner_cw', 
    'pressure_self_cw', 
    'pressure_partner_cw', 
    'pushing_self_cw', 
    'pushing_partner_cw', 
    'day', 
    'plan_selfPlan',
    'plan_partnerPlan', # todo: do we need this??
    'barriers_self_cw', 
    'facilitators_self_cw', 
    'weartime_self_cw',
    
    # '-- BETWEEN PERSON MAIN EFFECTS',
    'persuasion_self_cb',
    'persuasion_partner_cb',
    'pressure_self_cb',
    'pressure_partner_cb',
    'pushing_self_cb',
    'pushing_partner_cb',
    'barriers_self_cb', 
    'facilitators_self_cb', 
    'weartime_self_cb',
    
    # Interactions
    
    'persuasion_self_cw:barriers_self_cw',
    'barriers_self_cw:pressure_self_cw',
    'barriers_self_cw:pushing_self_cw',
    
    'persuasion_self_cw:facilitators_self_cw',
    'pressure_self_cw:facilitators_self_cw',
    'pushing_self_cw:facilitators_self_cw'
  )


model_rows_fixed_ordinal <- c(
  model_rows_fixed[1],
  'Intercept[1]',
  'Intercept[2]',
  'Intercept[3]',
  'Intercept[4]',
  'Intercept[5]',
  model_rows_fixed[2:length(model_rows_fixed)]
)

model_rows_random <- c(
  # '--------------',
  # '-- RANDOM EFFECTS --',
  'sd(Intercept)', 
  'sd(persuasion_self_cw)',
  'sd(persuasion_partner_cw)',
  'sd(pressure_self_cw)',
  'sd(pressure_partner_cw)',
  'sd(pushing_self_cw)',
  'sd(pushing_partner_cw)',
  
  'sd(barriers_self_cw)', 
  'sd(facilitators_self_cw)',
  
  'sd(persuasion_self_cw:barriers_self_cw)',
  'sd(barriers_self_cw:pressure_self_cw)',
  'sd(barriers_self_cw:pushing_self_cw)',
  
  'sd(persuasion_self_cw:facilitators_self_cw)',
  'sd(pressure_self_cw:facilitators_self_cw)',
  'sd(pushing_self_cw:facilitators_self_cw)',
  
  # '-- CORRELATION STRUCTURE -- ', 
  'sigma'
)

model_rows_random_ordinal <- c(model_rows_random,'disc')

```



```{r set_display_names_alt}

# For indistinguishable Dyads
model_rownames_fixed <- c(
    "Intercept", 
    # "-- WITHIN PERSON MAIN EFFECTS --", 
    "Daily individual's experienced persuasion",  
    "Daily partner's experienced persuasion", 
    "Daily individual's experienced pressure", 
    "Daily partner's experienced pressure", 
    "Daily individual's experienced pushing", 
    "Daily partner's experienced pushing", 
    "Day", 
    "Own actionplan",
    'Partner actionplan',
    "Daily barriers",
    "Daily facilitators",
    "Daily weartime",
    

    # "-- BETWEEN PERSON MAIN EFFECTS",
    "Mean individual's experienced persuasion", 
    "Mean partner's experienced persuasion", 
    "Mean individual's experienced pressure", 
    "Mean partner's experienced pressure", 
    "Mean individual's experienced pushing", 
    "Mean partner's experienced pushing", 
    'Mean barriers',
    "Mean facilitators",
    "Mean weartime",
    
    # Interactions
    'persuasion_self_cw:barriers_self_cw',
    'barriers_self_cw:pressure_self_cw',
    'barriers_self_cw:pushing_self_cw',
    
    'persuasion_self_cw:facilitators_self_cw',
    'pressure_self_cw:facilitators_self_cw',
    'pushing_self_cw:facilitators_self_cw'
  )


model_rownames_fixed_ordinal <- c(
  model_rownames_fixed[1],
  'Intercept[1]',
  'Intercept[2]',
  'Intercept[3]',
  'Intercept[4]',
  'Intercept[5]',
  model_rownames_fixed[2:length(model_rownames_fixed)]
)

model_rownames_random <- c(
  # '--------------',
  # '-- RANDOM EFFECTS --',
  'sd(Intercept)', 
  "sd(Daily individual's experienced persuasion)", 
  "sd(Daily partner's experienced persuasion)", # OR partner received
  "sd(Daily individual's experienced pressure)", 
  "sd(Daily partner's experienced pressure)", 
  "sd(Daily individual's experienced pushing)", 
  "sd(Daily partner's experienced pushing)", 
  
  'sd(barriers_self_cw)', 
  'sd(facilitators_self_cw)',
  
  'sd(persuasion_self_cw:barriers_self_cw)',
  'sd(barriers_self_cw:pressure_self_cw)',
  'sd(barriers_self_cw:pushing_self_cw)',
  
  'sd(persuasion_self_cw:facilitators_self_cw)',
  'sd(pressure_self_cw:facilitators_self_cw)',
  'sd(pushing_self_cw:facilitators_self_cw)',
  # '-- CORRELATION STRUCTURE -- ', 
  'sigma'
)

model_rownames_random_ordinal <- c(model_rownames_random,'disc')


```



```{r parameters_for_printing}

rows_to_pack <- list(
  "Within-Person Effects" = c(2,13),
  "Between-Person Effects" = c(14,22),
  "Interactions" = c(23, 28),
  "Random Effects" = c(29, 43), 
  "Additional Parameters" = c(44,44)
  )


rows_to_pack_ordinal <- list(
  "Within-Person Effects" = c(2+5,13+5),
  "Between-Person Effects" = c(14+5,22+5),
  "Interactions" = c(23+5, 28+5),
  "Random Effects" = c(29+5, 43+5), 
  "Additional Parameters" = c(44+5,44+6)
  )

```



## Self-Reported MVPA

```{r explore_pa_sub_dist}

range(df_double$pa_sub, na.rm = T) 
hist(df_double$pa_sub, breaks = 40) 

hist(log(df_double$pa_sub+00000000001), breaks = 40)

```

### Hurdle Lognormal Model
```{r pa_sub_lognormal, results='hide'}


formula <- bf(
  pa_sub ~ 
    persuasion_self_cw * barriers_self_cw + 
    pressure_self_cw * barriers_self_cw + 
    pushing_self_cw * barriers_self_cw + 
    
    persuasion_self_cw * facilitators_self_cw + 
    pressure_self_cw * facilitators_self_cw + 
    pushing_self_cw * facilitators_self_cw + 
    
    persuasion_partner_cw +
    pressure_partner_cw +
    pushing_partner_cw +
    
    persuasion_self_cb + persuasion_partner_cb +
    pressure_self_cb + pressure_partner_cb +
    pushing_self_cb + pushing_partner_cb +
    
    #plan_self + plan_partner +
    barriers_self_cb + 
    facilitators_self_cb + 
    day +  
    
    # Random effects
    (1 + persuasion_self_cw * barriers_self_cw + 
    pressure_self_cw * barriers_self_cw + 
    pushing_self_cw * barriers_self_cw + 
    
    persuasion_self_cw * facilitators_self_cw + 
    pressure_self_cw * facilitators_self_cw + 
    pushing_self_cw * facilitators_self_cw + 
    
    persuasion_partner_cw +
    pressure_partner_cw +
    pushing_partner_cw | dd | coupleID),
  
  hu = ~ persuasion_self_cw * barriers_self_cw + 
    pressure_self_cw * barriers_self_cw + 
    pushing_self_cw * barriers_self_cw + 
    
    persuasion_self_cw * facilitators_self_cw + 
    pressure_self_cw * facilitators_self_cw + 
    pushing_self_cw * facilitators_self_cw + 
    
    persuasion_partner_cw +
    pressure_partner_cw +
    pushing_partner_cw +
    
    persuasion_self_cb + persuasion_partner_cb +
    pressure_self_cb + pressure_partner_cb +
    pushing_self_cb + pushing_partner_cb +
    
    #plan_self + plan_partner +
    barriers_self_cb + 
    facilitators_self_cb + 
    day + 
    
    # Random effects
    (1 + persuasion_self_cw * barriers_self_cw + 
    pressure_self_cw * barriers_self_cw + 
    pushing_self_cw * barriers_self_cw + 
    
    persuasion_self_cw * facilitators_self_cw + 
    pressure_self_cw * facilitators_self_cw + 
    pushing_self_cw * facilitators_self_cw + 
    
    persuasion_partner_cw +
    pressure_partner_cw +
    pushing_partner_cw | dd | coupleID)
  
  , decomp = 'QR'
  #, autocor = autocor_str
) 

prior1 <- c(
  brms::set_prior("normal(0, 2.5)", class = "b")
  , brms::set_prior("normal(0, 2)", class = "b", dpar = "hu")
  , brms::set_prior("normal(0, 50)", class = "Intercept") # for non-zero PA
  , brms::set_prior("normal(0.5, 2.5)", class = "Intercept", dpar = 'hu') # hurdle part
  , brms::set_prior("normal(0, 2)", class = "sd", group = "coupleID", lb = 0)
  , brms::set_prior("student_t(3, 0, 2.5)", class = "sigma", lb = 0)
)

#brms::validate_prior(
#  prior1, 
#  formula = formula, 
#  data = df_double, 
#  family = hurdle_lognormal()
#)

#df_minimal <- df_double[, c("AorB", all.vars(as.formula(formula)))]

pa_sub <- my_brm(
  mi = use_mi, 
  imputed_data = implist,
  
  formula = formula, 
  prior = prior1,
  data = df_double, 
  family = brms::hurdle_lognormal(), 
  #family = brms::hurdle_negbinomial(), 
  #family = brms::hurdle_poisson(),
  control = list(adapt_delta = 0.90),
  iter = iterations,
  warmup = warmup,
  chains = 4,
  cores = 4,
  seed = 42,
  file = file.path("models_cache_brms", paste0("pa_sub_hu_lognormal", suffix))
  #, file_refit = 'always'
)


pa_sub_digest <- digest::digest(pa_sub)


```


```{r check_pa_sub_lognormal}
if (check_models) {
  check_brms(pa_sub, log_pp_check = TRUE)
  DHARMa.check_brms.all(pa_sub, integer = TRUE, outliers_type = 'bootstrap')
}
```


```{r check_pa_sub_lognormal_priorsense, cache=TRUE, cache.extra=c(pa_sub_digest, do_priorsense)}
if (do_priorsense) {
  priorsense_vars <- c(
      'Intercept',
      'b_persuasion_self_cw',
      'b_persuasion_partner_cw',
      'b_pressure_self_cw',
      'b_pressure_partner_cw',
      'b_pushing_self_cw',
      'b_pushing_partner_cw'
  )
  
  hurdle_priorsense_vars <- c(
    'Intercept_hu',
    'b_hu_persuasion_self_cw',
    'b_hu_persuasion_partner_cw',
    'b_hu_pressure_self_cw',
    'b_hu_pressure_partner_cw',
    'b_hu_pushing_self_cw',
    'b_hu_pushing_partner_cw'
  )
  
  gc()
  priorsense::powerscale_sensitivity(pa_sub, variable = c(priorsense_vars, hurdle_priorsense_vars))
  priorsense::powerscale_plot_dens(pa_sub, variable = c(priorsense_vars, hurdle_priorsense_vars))
  priorsense::powerscale_plot_ecdf(pa_sub, variable = c(priorsense_vars, hurdle_priorsense_vars))
  priorsense::powerscale_plot_quantities(pa_sub, variable = c(priorsense_vars, hurdle_priorsense_vars))
}

```


```{r report_pa_sub_lognormal, results='asis', fig.width=8, fig.height=7, dpi=300, cache=TRUE, cache.extra=c(pa_sub_digest, report_function_hash)}

# rope range for continuous part of the model
rope_factor <- sd(log(pa_sub$data$pa_sub[pa_sub$data$pa_sub > 0]))
rope_range_continuous = c(-0.1 * rope_factor, 0.1 * rope_factor)

summary_pa_sub <- summarize_brms(
  pa_sub, 
  stats_to_report = stats_to_report,
  rope_range = rope_range_continuous,
  hu_rope_range = c(-0.18, 0.18),
  model_rows_fixed = model_rows_fixed,
  model_rows_random = model_rows_random,
  model_rownames_fixed = model_rownames_fixed,
  model_rownames_random = model_rownames_random,
  exponentiate = T) 


# Print the updated dataframe
summary_pa_sub %>%
  print_df(rows_to_pack = rows_to_pack)


# Plot continuous part of model

variable <- c(
  '(Intercept)',
  'b_persuasion_self_cw',
  'b_persuasion_partner_cw',
  'b_pressure_self_cw',
  'b_pressure_partner_cw',
  'b_pushing_self_cw',
  'b_pushing_partner_cw'
)


plot(
  bayestestR::p_direction(pa_sub, parameter = variable),
  priors = TRUE
) + theme_bw()


plot(
  bayestestR::rope(
    pa_sub, 
    parameter = variable, 
    range = rope_range_continuous,
    verbose = F,
    ci = 1
  )
) + theme_bw()




# Hurdle part of the model
variable <- c(
  'b_hu_persuasion_self_cw',
  'b_hu_persuasion_partner_cw',
  'b_hu_pressure_self_cw',
  'b_hu_pressure_partner_cw',
  'b_hu_pushing_self_cw',
  'b_hu_pushing_partner_cw'
)

plot(
  bayestestR::p_direction(pa_sub, parameter = variable),
  priors = TRUE
) + theme_bw()

# The rope range for the bernoulli part of the model is -0.18, 0.18
plot(
  bayestestR::rope(pa_sub, parameter = variable, range = c(-0.18, 0.18), ci = 1),
  verbose = FALSE
) + theme_bw()


```


Hurdle part of the model on the left, non-zero part towards the right side of the table

```{r report_pa_sub_lognormald, fig.height=11, fig.width=12, dpi=600, results='asis', cache=TRUE, cache.extra=pa_sub_digest, warnings = FALSE}



conds_eff <- conditional_spaghetti(
  pa_sub, 
  effects = c(
    'persuasion_self_cw',
    'persuasion_partner_cw',
    'pressure_self_cw',
    'pressure_partner_cw',
    'pushing_self_cw',
    'pushing_partner_cw'
  ),
  x_label = c(
    'Received Persuasion',
    'Exerted Persuasion',
    'Received Pressure',
    'Exerted Pressure',
    'Received Plan-Related Pushing',
    'Exerted Plan-Related Pushing'
  ),
  group_var = 'coupleID',
  plot_full_range = TRUE,
  y_limits = c(0, 100),
  y_label = "Same-Day MVPA",
  y_labels = c('Probability of Being Active', 'Minutes of MVPA When Active', 'Overall Expected Minutes of MVPA'),
  , filter_quantiles = .9995
  , font_family = 'Candara'
)

print(conds_eff)

```
**Note.** This graphic illustrates the relationship between social control and moderate to vigorous physical activity (MVPA) using a Bayesian Hurdle-Lognormal Multilevel Model. The predictor is centered within individuals to examine how deviations from their average social control relate to same-day MVPA. Shaded areas indicate credible intervals, thick lines show fixed effects, and thin lines represent random effects, highlighting variability across couples.
The plots display the probability of being active, expected minutes of MVPA when active, and combined predicted MVPA. The bottom density plot visualizes the posterior distributions of slope estimates, transformed to represent multiplicative changes in odds ratios (hurdle component) or expected values. Medians and 95% credible intervals (2.5th and 97.5th percentiles) are shown. Effects are significant, when the 95% credible interval does not overlap 1.


### Comparing effect size of pressure and pushing

```{r compare_effects_pa_sub}

hypothesis(pa_sub, "pressure_self_cw < pushing_self_cw")

```




## Device Based MVPA 

```{r explore_pa_obj_dist}

range(df_double$pa_obj, na.rm = T) 

hist(df_double$pa_obj, breaks = 50)

df_double$pa_obj_log <- log(df_double$pa_obj)

hist(df_double$pa_obj_log, breaks = 50)

```



### Lognormal Model

```{r pa_obj_log_g, results='hide', message=FALSE}

formula <- bf(
  pa_obj ~ 
    persuasion_self_cw * barriers_self_cw + 
    pressure_self_cw * barriers_self_cw + 
    pushing_self_cw * barriers_self_cw + 
    
    persuasion_self_cw * facilitators_self_cw + 
    pressure_self_cw * facilitators_self_cw + 
    pushing_self_cw * facilitators_self_cw + 
    
    persuasion_partner_cw +
    pressure_partner_cw +
    pushing_partner_cw +
    
    persuasion_self_cb + persuasion_partner_cb +
    pressure_self_cb + pressure_partner_cb +
    pushing_self_cb + pushing_partner_cb +
    
    #plan_self + plan_partner +
    barriers_self_cb + 
    facilitators_self_cb + 
    day + weartime_self_cw + weartime_self_cb +
    
    # Random effects
    (1 + persuasion_self_cw * barriers_self_cw + 
    pressure_self_cw * barriers_self_cw + 
    pushing_self_cw * barriers_self_cw + 
    
    persuasion_self_cw * facilitators_self_cw + 
    pressure_self_cw * facilitators_self_cw + 
    pushing_self_cw * facilitators_self_cw + 
    
    persuasion_partner_cw +
    pressure_partner_cw +
    pushing_partner_cw | coupleID)
  
  , decomp = 'QR'
  #, autocor = autocor_str
)


prior1 <- c(
  brms::set_prior("normal(0, 2.5)", class = "b")
  , brms::set_prior("normal(0, 50)", class = "Intercept") 
  , brms::set_prior("normal(0, 2)", class = "sd", group = "coupleID", lb = 0)
  , brms::set_prior("student_t(3, 0, 2.5)", class = "sigma", lb = 0)
)


#brms::validate_prior(
#  prior1, 
#  formula = formula, 
#  data = df_double, 
#  family = lognormal()
#  )

#df_minimal <- df_double[, c("AorB", all.vars(as.formula(formula)))]

pa_obj_log <- my_brm(
  mi = use_mi, 
  imputed_data = implist,
  
  formula = formula, 
  prior = prior1,
  data = df_double, 
  family = lognormal(),
  control = list(adapt_delta = 0.99),
  iter = iterations + 200,
  warmup = warmup + 200,
  chains = 4,
  cores = 4,
  seed = 7777,
  file = file.path("models_cache_brms", paste0("pa_obj_log_gaussian", suffix))
  #, file_refit = 'always'
)

pa_obj_log_digest <- digest::digest(pa_obj_log)


```


```{r check_pa_obj_log_g}
if (check_models) {
  check_brms(pa_obj_log, log_pp_check = TRUE)
  DHARMa.check_brms.all(pa_obj_log, integer = TRUE, outliers_type = 'bootstrap')
}
```


```{r check_pa_obj_log_priorsense, cache=TRUE, cache.extra=c(pa_obj_log_digest, do_priorsense)}
if (do_priorsense) {
  gc()
  priorsense::powerscale_sensitivity(pa_obj_log, variable = priorsense_vars)
  priorsense::powerscale_plot_dens(pa_obj_log, variable = priorsense_vars)
  priorsense::powerscale_plot_ecdf(pa_obj_log, variable = priorsense_vars)
  priorsense::powerscale_plot_quantities(pa_obj_log, variable = priorsense_vars)
}

```



```{r report_pa_obj_log_g, results='asis', cache=TRUE, cache.extra=c(pa_obj_log_digest, report_function_hash)}

# rope range for lognormal model
rope_factor <- sd(log(pa_obj_log$data$pa_obj))
rope_range_log = c(-0.1 * rope_factor, 0.1 * rope_factor)

summary_pa_obj <- summarize_brms(
  pa_obj_log, 
  stats_to_report = stats_to_report,
  rope_range = rope_range_log,
  model_rows_fixed = model_rows_fixed,
  model_rows_random = model_rows_random,
  model_rownames_fixed = model_rownames_fixed,
  model_rownames_random = model_rownames_random,
  exponentiate = T) 

summary_pa_obj %>%
  print_df(rows_to_pack = rows_to_pack)


plot(
  bayestestR::p_direction(pa_obj_log),
  priors = TRUE
) + 
  coord_cartesian(xlim = c(-3, 3)) +
  theme_bw()


plot(
  bayestestR::rope(pa_obj_log, range = rope_range_log, ci = 1)
) + theme_bw()



# Nothing significant, no plots

```


## Affect

```{r explore_aff_dist}

range(df_double$aff, na.rm = T)
hist(df_double$aff, breaks = 15)

```

### Gaussian
```{r mood_gauss, results='hide', results='hide', message=FALSE}


formula <- bf(
  aff ~ 
    persuasion_self_cw * barriers_self_cw + 
    pressure_self_cw * barriers_self_cw + 
    pushing_self_cw * barriers_self_cw + 
    
    persuasion_self_cw * facilitators_self_cw + 
    pressure_self_cw * facilitators_self_cw + 
    pushing_self_cw * facilitators_self_cw + 
    
    persuasion_partner_cw +
    pressure_partner_cw +
    pushing_partner_cw +
    
    persuasion_self_cb + persuasion_partner_cb +
    pressure_self_cb + pressure_partner_cb +
    pushing_self_cb + pushing_partner_cb +
    
    #plan_self + plan_partner +
    barriers_self_cb + 
    facilitators_self_cb + 
    day + 
    
    # Random effects
    (1 + persuasion_self_cw * barriers_self_cw + 
    pressure_self_cw * barriers_self_cw + 
    pushing_self_cw * barriers_self_cw + 
    
    persuasion_self_cw * facilitators_self_cw + 
    pressure_self_cw * facilitators_self_cw + 
    pushing_self_cw * facilitators_self_cw + 
    
    persuasion_partner_cw +
    pressure_partner_cw +
    pushing_partner_cw | coupleID)
  
  , decomp = 'QR'
  #, autocor = autocor_str
)


prior1 <- c(
  brms::set_prior("normal(0, 5)", class = "b")
  ,brms::set_prior("normal(0, 20)", class = "Intercept", lb=1, ub=6)
  , brms::set_prior("normal(0, 2)", class = "sd", group = "coupleID", lb = 0)
  , brms::set_prior("student_t(3, 0, 2.5)", class = "sigma", lb = 0)
)

#brms::validate_prior(
#  prior1, 
#  formula = formula, 
#  data = df_double, 
#  family = gaussian()
#  )

#df_minimal <- df_double[, c("AorB", all.vars(as.formula(formula)))]

mood_gauss <- my_brm(
  mi = use_mi, 
  imputed_data = implist,
  
  formula = formula, 
  prior = prior1,
  data = df_double, 
  family = gaussian(),
  control = list(adapt_delta = 0.95),
  iter = iterations,
  warmup = warmup,
  chains = 4,
  cores = 4,
  seed = 7777,
  file = file.path("models_cache_brms", paste0("mood_gauss", suffix))
  #, file_refit = 'always'
)

mood_gauss_digest <- digest::digest(mood_gauss)


```


```{r check_mood_gauss}
if (check_models) {
  check_brms(mood_gauss, log_pp_check = FALSE)
  DHARMa.check_brms.all(mood_gauss, integer = FALSE)
}
```


```{r check_mood_gauss_priorsense, cache=TRUE, cache.extra=c(mood_gauss_digest, do_priorsense)}

if (do_priorsense) {
  gc()
  priorsense::powerscale_sensitivity(mood_gauss, variable = priorsense_vars)
  priorsense::powerscale_plot_dens(mood_gauss, variable = priorsense_vars)
  priorsense::powerscale_plot_ecdf(mood_gauss, variable = priorsense_vars)
  priorsense::powerscale_plot_quantities(mood_gauss, variable = priorsense_vars)
}

```

```{r report_mood_gauss, results='asis', fig.width=8, fig.height=6, dpi=300, cache=TRUE, cache.extra=c(mood_gauss_digest, report_function_hash)}

summary_mood <- summarize_brms(
  mood_gauss, 
  stats_to_report = stats_to_report,
  model_rows_fixed = model_rows_fixed,
  model_rows_random = model_rows_random,
  model_rownames_fixed = model_rownames_fixed,
  model_rownames_random = model_rownames_random,
  exponentiate = F) 

summary_mood %>%
  print_df(rows_to_pack = rows_to_pack)


plot(
  bayestestR::p_direction(mood_gauss),
  priors = TRUE
)  + 
  coord_cartesian(xlim = c(-3, 3)) +
  theme_bw()

plot(
  bayestestR::rope(mood_gauss, ci = 1)
) + theme_bw()


conditional_spaghetti(
  mood_gauss, 
  effects = c('pushing_partner_cw'),
  group_var = 'coupleID',
  plot_full_range = TRUE
)

```




## Reactance

```{r investigatee_reactance}

range(df_double$reactance, na.rm = T) 
hist(df_double$reactance, breaks = 7) 

hist(log(df_double$reactance+0.1), breaks = 10)

```


### Ordinal

```{r reactance_ordinal, results='hide', message=FALSE}

df_double$reactance_ordinal <- factor(df_double$reactance,
                                      levels = 0:5, 
                                      ordered = TRUE)

formula <- bf(
  reactance_ordinal ~ 
    persuasion_self_cw * barriers_self_cw + 
    pressure_self_cw * barriers_self_cw + 
    pushing_self_cw * barriers_self_cw + 
    
    persuasion_self_cw * facilitators_self_cw + 
    pressure_self_cw * facilitators_self_cw + 
    pushing_self_cw * facilitators_self_cw + 
    
    persuasion_partner_cw +
    pressure_partner_cw +
    pushing_partner_cw +
    
    persuasion_self_cb + persuasion_partner_cb +
    pressure_self_cb + pressure_partner_cb +
    pushing_self_cb + pushing_partner_cb +
    
    #plan_self + plan_partner +
    barriers_self_cb + 
    facilitators_self_cb + 
    day + 
    
    # Random effects
    (1 + persuasion_self_cw * barriers_self_cw + 
    pressure_self_cw * barriers_self_cw + 
    pushing_self_cw * barriers_self_cw + 
    
    persuasion_self_cw * facilitators_self_cw + 
    pressure_self_cw * facilitators_self_cw + 
    pushing_self_cw * facilitators_self_cw + 
    
    persuasion_partner_cw +
    pressure_partner_cw +
    pushing_partner_cw | coupleID)
  
  , decomp = 'QR'
  #, autocor = autocor_str
)


prior1 <- c(
  brms::set_prior("normal(0, 2.5)", class = "b")
  , brms::set_prior("normal(0, 2)", class = "sd", group = "coupleID", lb = 0)
)


#brms::validate_prior(
#  prior1, 
#  formula = formula, 
#  data = df_double, 
#  family = cumulative() # HURDLE_CUMULATIVE
#  )


#df_minimal <- df_double[, c("AorB", all.vars(as.formula(formula)))]

reactance_ordinal <- my_brm(
  mi = use_mi, 
  imputed_data = implist,
  
  formula = formula, 
  prior = prior1,
  data = df_double, 
  family = brms::cumulative(),
  #control = list(adapt_delta = 0.95),
  iter = iterations,
  warmup = warmup,
  chains = 4,
  cores = 4,
  seed = 7777
  , file = file.path("models_cache_brms", paste0("reactance_ordinal", suffix))
)


reactance_ordinal_digest <- digest::digest(reactance_ordinal)


```


```{r check_reactance_ordinal}
if (check_models) {
  check_brms(reactance_ordinal)
  DHARMa.check_brms.all(reactance_ordinal, outliers_type = 'bootstrap')
}
```


```{r check_reactance_ordinal_priorsense, cache=TRUE, cache.extra=c(reactance_ordinal_digest, do_priorsense)}

if (do_priorsense) {
  gc()
  priorsense::powerscale_sensitivity(reactance_ordinal, variable = priorsense_vars)
  priorsense::powerscale_plot_dens(reactance_ordinal, variable = priorsense_vars)
  priorsense::powerscale_plot_ecdf(reactance_ordinal, variable = priorsense_vars)
  priorsense::powerscale_plot_quantities(reactance_ordinal, variable = priorsense_vars)
}

```

```{r report_reactance_ordinal, results='asis', fig.width=8, fig.height=6, dpi=300, cache=TRUE, cache.extra=c(reactance_ordinal_digest, report_function_hash)}

summary_reactance_ordinal <- summarize_brms(
  reactance_ordinal, 
  stats_to_report = stats_to_report,
  rope_range = c(-0.18, 0.18),
  model_rows_fixed = model_rows_fixed_ordinal,
  model_rows_random = model_rows_random_ordinal,
  model_rownames_fixed = model_rownames_fixed_ordinal,
  model_rownames_random = model_rownames_random_ordinal,
  exponentiate = T) 

summary_reactance_ordinal %>%
  print_df(rows_to_pack = rows_to_pack_ordinal)


plot(
  bayestestR::p_direction(reactance_ordinal),
  priors = TRUE
) + 
  coord_cartesian(xlim = c(-6, 6)) +
  theme_bw()

plot(
  bayestestR::rope(reactance_ordinal, range = c(-0.18, 0.18), ci = 1)
) + theme_bw()



#conditional_spaghetti(
#  reactance_ordinal, 
#  effects = c('persuasion_self_cw', 'pressure_self_cw')
#  , group_var = 'coupleID'
#  #, n_groups = 15
#  , plot_full_range = T
#)


```


### Binary 

```{r is_reactance, results='hide', message=FALSE}

introduce_binary_reactance <- function(data) {
  data$is_reactance <- factor(data$reactance > 0, levels = c(FALSE, TRUE), labels = c(0, 1))
  return(data)
}



df_double <- introduce_binary_reactance(df_double)
if (use_mi) {
  for (i in seq_along(implist)) {
    implist[[i]] <- introduce_binary_reactance(implist[[i]])
  }
}


formula <- bf(
  is_reactance ~ 
    persuasion_self_cw * barriers_self_cw + 
    pressure_self_cw * barriers_self_cw + 
    pushing_self_cw * barriers_self_cw + 
    
    persuasion_self_cw * facilitators_self_cw + 
    pressure_self_cw * facilitators_self_cw + 
    pushing_self_cw * facilitators_self_cw + 
    
    persuasion_partner_cw +
    pressure_partner_cw +
    pushing_partner_cw +
    
    persuasion_self_cb + persuasion_partner_cb +
    pressure_self_cb + pressure_partner_cb +
    pushing_self_cb + pushing_partner_cb +
    
    #plan_self + plan_partner +
    barriers_self_cb + 
    facilitators_self_cb + 
    day + 
    
    # Random effects
    (1 + persuasion_self_cw * barriers_self_cw + 
    pressure_self_cw * barriers_self_cw + 
    pushing_self_cw * barriers_self_cw + 
    
    persuasion_self_cw * facilitators_self_cw + 
    pressure_self_cw * facilitators_self_cw + 
    pushing_self_cw * facilitators_self_cw + 
    
    persuasion_partner_cw +
    pressure_partner_cw +
    pushing_partner_cw | coupleID)
  
  , decomp = 'QR'
  #, autocor = autocor_str
  )



prior1 <- c(
  brms::set_prior("normal(0, 2.5)", class = "b")
  , brms::set_prior("normal(0, 10)", class = "Intercept", lb=0, ub=5) 
  , brms::set_prior("normal(0, 2)", class = "sd", group = "coupleID", lb = 0)
)


#brms::validate_prior(
#  prior1, 
#  formula = formula, 
#  data = df_double, 
#  family = bernoulli()
#  )



#df_minimal <- df_double[, c("AorB", all.vars(as.formula(formula)))]

is_reactance <- my_brm(
  mi = use_mi, 
  imputed_data = implist,
  
  formula = formula, 
  prior = prior1,
  data = df_double, 
  family = brms::bernoulli(),
  #control = list(adapt_delta = 0.95, max_treedepth = 15),
  iter = iterations,
  warmup = warmup,
  chains = 4,
  cores = 4,
  seed = 7777,
  file = file.path("models_cache_brms", paste0("is_reactance", suffix))
  #, file_refit = 'always'
)

is_reactance_digest <- digest::digest(is_reactance)

```

```{r check_is_reactance}
if (check_models) {
  check_brms(is_reactance)
  DHARMa.check_brms.all(is_reactance, integer = FALSE)
}
```


```{r check_is_reactance_priorsense, cache=TRUE, cache.extra=c(is_reactance_digest, do_priorsense)}
if (do_priorsense) {
  gc()
  priorsense::powerscale_sensitivity(is_reactance, variable = priorsense_vars)
  priorsense::powerscale_plot_dens(is_reactance, variable = priorsense_vars)
  priorsense::powerscale_plot_ecdf(is_reactance, variable = priorsense_vars)
  priorsense::powerscale_plot_quantities(is_reactance, variable = priorsense_vars)
}

```

```{r report_is_reactance, results='asis', fig.width=8, fig.height=6, dpi=300, cache=TRUE, cache.extra=c(is_reactance_digest, report_function_hash)}

summary_is_reactance <- summarize_brms(
  is_reactance, 
  stats_to_report = stats_to_report,
  model_rows_fixed = model_rows_fixed,
  model_rows_random = model_rows_random,
  model_rownames_fixed = model_rownames_fixed,
  model_rownames_random = model_rownames_random,
  exponentiate = T) 

summary_is_reactance %>%
  print_df(rows_to_pack = rows_to_pack)

plot(
  bayestestR::p_direction(is_reactance),
  priors = TRUE
) + 
  coord_cartesian(xlim = c(-6, 6)) +
  theme_bw()

plot(
  bayestestR::rope(is_reactance, ci = 1)
) + theme_bw()



conditional_spaghetti(
  is_reactance, 
  effects = c('pressure_self_cw', 'pushing_self_cw'),
  group_var = 'coupleID',
  plot_full_range = TRUE
)

```


```{r testingdifferencecoefsbinary}

hypothesis(is_reactance, "exp(pressure_self_cw) > exp(pushing_self_cw)")

```



# Report All Models

```{r report_sidebyside, results = 'asis'}

summary_all_models <- report_side_by_side(
  pa_sub,
  pa_obj_log,
  mood_gauss,
  is_reactance,
  
  stats_to_report = c('CI'),
  model_rows_random = model_rows_random,
  model_rows_fixed = model_rows_fixed,
  model_rownames_random = model_rownames_random,
  model_rownames_fixed = model_rownames_fixed
)

summary_all_models <- summary_all_models %>%
  print_df(rows_to_pack = rows_to_pack) %>%
  add_header_above(
    c(
      " ", "Hurdle Component" = 2, "Non-Zero Component" = 2,
      " " = 6
    )
  ) %>%
  add_header_above(
    c(" ", "Subjective MVPA Hurdle Lognormal" = 4,  
      "Device-Based MVPA Log (Gaussian)" = 2, 
      "Mood Gaussian" = 2,
      #"Reactance Ordinal" = 2,
      "Reactance Dichotome" = 2
    )
  )

export_xlsx(
  summary_all_models, 
  rows_to_pack = rows_to_pack,
  file.path("Output", paste0("AllModels", suffix, ".xlsx")), 
  merge_option = 'both', 
  simplify_2nd_row = FALSE,
  line_above_rows = c(1,2),
  line_below_rows = c(-1)
)

  
summary_all_models

```

Plot Interaction effect. 

1. Probability of being active (crossing the hurdle)

```{r}

library(ggplot2)
library(plotly)


p <- conditional_effects(
  pa_sub, 
  dpar = 'hu',
  effects = 'pushing_self_cw:barriers_self_cw',
  re_formula = NA, 
  method = 'posterior_linpred',
  plot = FALSE
)

p2 <- p

p2[[1]]$estimate__ <- 1 - p[[1]]$estimate__
p2[[1]]$lower__ <- 1 - p[[1]]$upper__
p2[[1]]$upper__ <- 1 - p[[1]]$lower__

plot(p2)


```

# Test slope of pushing at high levels of barriers

```{r}


library(tidybayes)
library(dplyr)
library(ggplot2)

plot_slope_by_moderator <- function(
  mod,            
  df,             
  moderator,      
  predictor_par,  
  interaction_par,
  exponentiate = FALSE,   
  n_points = 1000,
  fill_colors = c("Significant" = "steelblue",
                  "Non-significant" = "coral"),
  line_colors = fill_colors,  # Reuse fill colors by default
  vjust_val = -1.5
) {
  
  # Generate a sequence of moderator values
  moderator_seq <- seq(
    from = min(df[[moderator]], na.rm = TRUE),
    to = max(df[[moderator]], na.rm = TRUE),
    length.out = n_points
  )
  
  # Extract posterior draws for the parameters of interest
  library(rlang)
  predictor_sym <- rlang::sym(predictor_par)
  interaction_sym <- rlang::sym(interaction_par)

  post_draws <- mod %>%
    spread_draws(!!predictor_sym, !!interaction_sym)
  
  # For each moderator value, compute the slope for each posterior draw
  slope_list <- lapply(moderator_seq, function(mod_val) {
    tibble(
      moderator_value = mod_val,
      slope = - (post_draws[[predictor_par]] + mod_val * post_draws[[interaction_par]])
    )
  })
  
  # Combine the list into a single data frame
  slope_df <- bind_rows(slope_list)
  
  # Summarize the posterior for each moderator value (using a 95% credible interval)
  slope_summary <- slope_df %>%
    group_by(moderator_value) %>%
    summarize(
      slope_median = median(slope),
      slope_lower  = quantile(slope, probs = 0.025),
      slope_upper  = quantile(slope, probs = 0.975)
    ) %>%
    # Create significance flag: "sig" if CI excludes 0, "ns" otherwise
    mutate(sig_flag = if_else(slope_lower > 0 | slope_upper < 0, "sig", "ns")) %>%
    arrange(moderator_value)
  
  # If exponentiate == TRUE, transform slope columns
  if (exponentiate) {
    slope_summary <- slope_summary %>%
      mutate(
        slope_median_exp = exp(slope_median),
        slope_lower_exp  = exp(slope_lower),
        slope_upper_exp  = exp(slope_upper)
      )
  }
  
  # Identify boundary rows and duplicate them for each category
  slope_summary <- slope_summary %>%
    mutate(
      next_sig_flag = lead(sig_flag),
      is_boundary   = sig_flag != next_sig_flag & !is.na(next_sig_flag)
    )
  
  boundary_rows <- slope_summary %>%
    filter(is_boundary)
  
  boundary_rows_next <- boundary_rows
  boundary_rows_next$sig_flag <- boundary_rows_next$next_sig_flag
  
  slope_summary_extended <- bind_rows(slope_summary, boundary_rows_next)
  
  # Split into "sig" and "ns"
  slope_summary_sig <- slope_summary_extended %>% filter(sig_flag == "sig")
  slope_summary_ns  <- slope_summary_extended %>% filter(sig_flag == "ns")
  
  # Build the base plot:
  #    We'll use either slope_{median, lower, upper} or slope_{median_exp, lower_exp, upper_exp} 
  #    depending on exponentiate.
  if (exponentiate) {
    median_col <- "slope_median_exp"
    lower_col <- "slope_lower_exp"
    upper_col <- "slope_upper_exp"
    y_lab <- "Odds Ratio (Exponentiated Slope)"
    ref_line <- 1  # reference line for ORs is 1
  } else {
    median_col <- "slope_median"
    lower_col <- "slope_lower"
    upper_col <- "slope_upper"
    y_lab <- "Slope (Log-Odds Scale)"
    ref_line <- 0
  }
  
  p <- ggplot() +
    # Non-significant region
    geom_ribbon(
      data = slope_summary_ns,
      aes_string(
        x = "moderator_value",
        ymin = lower_col,
        ymax = upper_col,
        fill = '"Non-significant"'
      ),
      alpha = 0.2
    ) +
    geom_line(
      data = slope_summary_ns,
      aes_string(
        x = "moderator_value",
        y = median_col,
        color = '"Non-significant"'
      ),
      size = 1
    ) +
    # Significant region
    geom_ribbon(
      data = slope_summary_sig,
      aes_string(
        x = "moderator_value",
        ymin = lower_col,
        ymax = upper_col,
        fill = '"Significant"'
      ),
      alpha = 0.2
    ) +
    geom_line(
      data = slope_summary_sig,
      aes_string(
        x = "moderator_value",
        y = median_col,
        color = '"Significant"'
      ),
      size = 1
    ) +
    # Reference line (0 for log-odds, 1 for odds-ratios)
    geom_hline(
      yintercept = ref_line, 
      linetype = "dashed"
    ) +
    # Manual scales for fill & color
    scale_fill_manual(
      values = fill_colors
    ) +
    scale_color_manual(
      values = line_colors
    ) +
    labs(
      x = moderator,
      y = y_lab,
      fill = "Significance",
      color = "Significance"
    ) +
    theme_minimal()
  
  # Add boundary lines (where significance changes) & labels
  p2 <- p +
    geom_vline(
      data = boundary_rows,
      aes(xintercept = moderator_value),
      color = fill_colors["Significant"],
      alpha = 0.35,
      size = 0.7,
      linetype = "dashed"
    ) +
    geom_text(
      data = boundary_rows,
      aes(x = moderator_value, y = -Inf, label = round(moderator_value, 3)),
      vjust = vjust_val,
      size  = 3.7
    )
  
  return(p2)
}


p_log_odds <- plot_slope_by_moderator(
  mod = pa_sub, 
  df = df_double, 
  moderator = "barriers_self_cw", 
  predictor_par = "b_hu_pushing_self_cw", 
  interaction_par = "b_hu_barriers_self_cw:pushing_self_cw",
  exponentiate = FALSE
)

p_log_odds

p_odds_ratio <- plot_slope_by_moderator(
  mod = pa_sub, 
  df = df_double, 
  moderator = "barriers_self_cw", 
  predictor_par = "b_hu_pushing_self_cw", 
  interaction_par = "b_hu_barriers_self_cw:pushing_self_cw",
  exponentiate = TRUE,
  vjust_val = -12,
) + coord_cartesian(ylim = c(1, 18))

p_odds_ratio


# Export
ggsave(
  filename = file.path("Output", "InteractPlot_log_odds.png"), 
  plot = p_log_odds,
  width = 8,
  height = 5,
  dpi = 300
)

ggsave(
  filename = file.path("Output", "InteractPlot_odds_ratio.png"), 
  plot = p_odds_ratio, 
  width = 8, 
  height = 5, 
  dpi = 300
)


```


2. Expected MVPA when the hurdle was crossed (interaction NOT significant)

```{r}

p3 <- conditional_effects(
  pa_sub, 
  dpar = 'mu',
  effects = 'pushing_self_cw:barriers_self_cw',
  #re_formula = NULL, 
  plot = FALSE
)

p3[[1]]$estimate__ <- exp(p3[[1]]$estimate__)
p3[[1]]$lower__ <- exp(p3[[1]]$lower__)
p3[[1]]$upper__ <- exp(p3[[1]]$upper__)

plot(p3, ask = FALSE)
```


2. Expected physical activity in Minutes (when both components combined)

```{r}
# Expected physical activity
p4 <- conditional_effects(
  pa_sub, 
  effects = 'pushing_self_cw:barriers_self_cw',
  #re_formula = NULL,
  plot = FALSE
)

plot(p4, ask = FALSE)

```


```{r report_system, results='asis'}

report::report_system()
report::report_packages()
report::cite_packages()

```


```{r shut_system_down, results='hide', echo=FALSE, message=FALSE}

if (shutdown) {
  system("shutdown /s /t 180")
}

beepr::beep(sound = 3)

```


