---
title: "Social Control - Descriptives"
author: "Pascal Küng, MSc, Patrick Höhener, MSc, James M. Allen, PhD, Robert Tobias, PhD, Urte Scholz, PhD"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_document:
    theme: flatly
    df_print: kable
    toc: yes
    toc_float:
      collapsed: false
      smooth_scroll: true
    code_folding: show
    toc_depth: 5
    highlight: tango
---

```{r setup, message=FALSE, results='hide'}
library(tidyverse)
library(wbCorr)

knitr::opts_chunk$set(echo = TRUE)

source(file.path('Functions', 'ReportModels.R'))
source(file.path('Functions', 'PrettyTables.R'))
source(file.path('Functions', 'ReportMeasures.R'))
source(file.path('Functions', 'PrepareData.R'))
```


```{r prepare_datasets, results='hide'}

df <- openxlsx::read.xlsx(file.path('long.xlsx'))
df_original <- df

dfs <- prepare_data(df, recode_pushing = TRUE, use_mi = FALSE)
df_double <- dfs[[1]]
df_full <- dfs[[2]]

```


# Sample Statistics

```{r sample_desc, results='asis'}
# Sample Statistics

# Income (mean of both partner's report)
merge_income <- function(income1, income2) {
  merged_income <- numeric(length(income1))
  
  # Loop through each pair of incomes
  for (i in seq_along(income1)) {
    # Handle NA
    if (is.na(income1[i])) {
      merged_income[i] <- income2[i]
    } 
    
    else if (is.na(income2[i])) {
      merged_income[i] <- income1[i]
    }
    
    # if both are informative, take mean and round
    else if (income1[i] %in% 1:6 && income2[i] %in% 1:6) {
      merged_income[i] <- round((income1[i] + income2[i]) / 2)
    }
    
    # if one is informative and the other not, use the informative one. 
    else if (income1[i] %in% 1:6) {
      merged_income[i] <- income1[i]
    }
    else if (income2[i] %in% 1:6) {
      merged_income[i] <- income2[i]
    }
    
    # Now we only have cases, where both are either 70 or 99. We simply report "Undisclosed". 
    else {
      merged_income[i] <- 99
    }
  }
  
  # Convert to factor
  merged_income <- factor(
    merged_income, levels = c(1,2,3,4,5,6,70,99), 
    labels = c(
      "Up to CHF 2'000", 
      "CHF 2'001 to CHF 4'000",
      "CHF 4'001 to CHF 6'000",
      "CHF 6'001 to CHF 8'000",
      "CHF 8'001 to CHF 10'000", 
      "Above CHF 10'000", 
      "I do not know",
      "Undisclosed"
  )
  )
  
  return(merged_income)
}

df_sample_report <- df_full %>%
  group_by(coupleID) %>%
  arrange(userID) %>%
  # Computing couple level variables
  mutate(
    "Household income" = merge_income(first(pre_income_1), last(pre_income_1)),
    
    reldur = pre_rel_duration_m / 12 + pre_rel_duration_y,
    "Relationship duration" = mean(reldur, na.rm = TRUE),
    
    habdur = pre_hab_duration_m / 12 + pre_hab_duration_y,
    "Cohabiting duration" = mean(habdur, na.rm = TRUE),
    
    "Marital status" = factor(
      case_when(
        all(pre_mat_stat == 1) ~ "Married",
        any(pre_mat_stat == 1) ~ "One partner married",
        TRUE ~ "Not married"
      )
    ),
    
    "Have children" = factor(
      (first(pre_child_option) + last(pre_child_option)) > 0, 
      levels = c(FALSE, TRUE), 
      labels = c("Have children", "No children")),
    
    Gender = factor(
      gender, 
      levels = c(1,2,3), 
      labels = c("Male", "Female", "Other")),
    
    "Couple type" = as.factor(
      case_when(
        first(Gender) == last(Gender) & first(Gender) == "Male" ~ "Same-sex couple (male)",
        first(Gender) == last(Gender) & first(Gender) == "Female" ~ "Same-sex couple (female)",
        TRUE ~ "Mixed-sex couple"
      )
    )
  ) %>%
  ungroup() %>%
  # Individual level variables
  mutate(
    Age = pre_age,
    Handedness = factor(
      pre_handedness, 
      levels = c(0, 1, 2), 
      labels = c("Right", "Left", "Ambidextrous")),
  "Highest education" = factor(
    pre_education, 
    levels = c(1,2,3,4,5,6,7), 
    labels = c(
      "(Still) no school diploma",
      "Compulsory education (9 years)",
      "Vocational training (apprenticeship)",
      "Matura (university entrance qualification)",
      "Bachelor's degree", 
      "Master's degree",
      "Doctorate degree"
      )
    ),
  BMI = pre_weight / ((pre_height / 100)^2) # to meters
  ) %>%
  select(c("Relationship duration", "Cohabiting duration", "Couple type", "Household income", 
            "Marital status", "Have children", 
            Gender, Age, Handedness, "Highest education", BMI))


sample_table <- report_measures(df_sample_report, ICC = F)
sample_table$n_Obs <- as.numeric(sample_table$n_Obs) / 55
rownames(sample_table) <- NULL

n_couple_vars <- 17
sample_table$n_Obs[1:n_couple_vars] <- sample_table$n_Obs[1:n_couple_vars] / 2

names(sample_table) <- c('Variable', 'Level', 'n Observations', '% Observations', 'Missing', 'Mean', 'SD', 'Range')

packing_sample <- list(
    "Couple level variables (38 couples)" = 
      c(1, n_couple_vars),
    "Individual level variables (76 individuals)" 
    = c(n_couple_vars+1, nrow(sample_table))
    ) 

df_sample_summary <- print_df(
  sample_table,
  rows_to_pack = packing_sample
)


export_xlsx(df_sample_summary,
            file.path('Output', 'SampleDescription.xlsx'),
            merge_option = 'both',
            rows_to_pack = packing_sample,
            colwidths = c(20,35,7,7,7,7,7,10),
            simplify_2nd_row = FALSE,
            line_above_rows = c(0,1),
            line_below_rows = c(-1)
            )

df_sample_summary



```


# Measures Descriptives
## Focal Variables

```{r measures_desc, results='asis'}


main_constructs <- c("persuasion", "pressure","pushing", 
                     "pa_sub", "pa_obj", "aff", "reactance"
                     )

main_descriptives <- report_measures(
  data = df_full, 
  measures = main_constructs,
  ICC = TRUE, 
  cluster_var = df_full$userID)

names(main_descriptives) <- c('Variable', 'n Observations', 'Missing', 'Mean', 'SD', 'Range')


df_main_descriptives <- print_df(
  main_descriptives
)


export_xlsx(
  df_main_descriptives,
  file.path('Output', 'DescriptivesMain.xlsx'),
  merge_option = 'both',
  #colwidths = c(20,35,7,7,7,7,7,10),
  simplify_2nd_row = FALSE,
  line_above_rows = c(0,1),
  line_below_rows = c(-1)
)

df_main_descriptives


```

## All Variables

```{r measuers_all_desc, results='asis'}

all_constructs <- c(
  main_constructs,
  "day",
  "weartime",
  "isWeekend",
  "plan",
  "studyGroup",
  "support",
  "got_JITAI",
  "skilled_support"
)


all_descriptives <- report_measures(df_full, all_constructs, ICC = F)

names(all_descriptives) <- c('Variable', 'Level', 'n Observations', '% Observations', 'Missing', 'Mean', 'SD', 'Range')

df_all_descriptives <- print_df(
  all_descriptives
)


export_xlsx(
  df_all_descriptives,
  file.path('Output', 'DescriptivesAll.xlsx'),
  merge_option = 'both',
  #colwidths = c(20,35,7,7,7,7,7,10),
  simplify_2nd_row = FALSE,
  line_above_rows = c(0,1),
  line_below_rows = c(-1)
)

df_all_descriptives


```



# Correlations between self-report and partner-report

```{r corrs_measures_self_partner, results='asis'}

same_constr <- c(
  'ss_psc_more', 'sp_psc_more',
  'ss_nsc_more', 'sp_nsc_more',
  'ss_push_plan', 'sp_push_plan')

cors <- wbCorr(
  df_original[,c(same_constr)], 
  df_original$coupleID, 
  method = 'spearman')

self_partner_report_cors <- summary(cors, 'wb')

to_excel(
  self_partner_report_cors,
  file.path('Output', 'SelfVsPartnerReport.xlsx')
)


print_df(self_partner_report_cors[[1]], width = '7em')

```

Within-person correlations are above the diagonal and between-person correlations are below the diagonal.
On the diagonal are intraclass correlations (ICCs)



# Correlations Measure

```{r corrs, results='asis'}

cors <- wbCorr(
  df_full[,c(main_constructs)], 
  df_full$coupleID, 
  method = 'spearman')

main_cors <- summary(cors, 'wb')

to_excel(
  main_cors,
  file.path('Output', 'CorrelationsMain.xlsx')
)


print_df(main_cors[[1]], width = '7em')

cors <- wbCorr(
  df_full[,c(all_constructs)], 
  df_full$coupleID, 
  method = 'spearman')

full_cors <- summary(cors, 'wb')


to_excel(
  full_cors,
  file.path('Output', 'CorrelationsAll.xlsx')
)


print_df(full_cors[[1]], width = '7em')

```

Within-person correlations are above the diagonal and between-person correlations are below the diagonal.
On the diagonal are intraclass correlations (ICCs)



```{r report_system, results='asis'}

report::report_system()
report::report_packages()
report::cite_packages()

```

